### 2019-04-11 paper.tex
Extract from the previous paper.

\documentclass[jocse]{jocseart}

\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% Copyright
\setcopyright{jocsecopyright}
\jocseDOI{10.22369/issn.2153-4136/x/x/x }

\pagestyle{plain}
\pagenumbering{gobble}

\usepackage{cleveref}

\usepackage{graphicx}
\graphicspath{{./fig/}}
\DeclareGraphicsExtensions{.png,.pdf,.jpg,.jpeg}

\begin{document}
\title{Looking Back: One Year HPC Certification Forum}

\author{Julian Kunkel}
\affiliation{%
  \institution{University of Reading}
  \streetaddress{}
  \city{Reading}
  \state{United Kingdom}
  \postcode{}
}
\email{j.m.kunkel@reading.ac.uk}

\author{Kai Himstedt}
\author{Nathanael Hübbe}
\affiliation{%
  \institution{Universität Hamburg}
  \streetaddress{}
  \city{Hamburg}
  \state{Germany}
  \postcode{}
}

\author{Weronika Filinger}
\affiliation{%
  \institution{EPCC, The University of Edinburgh}
  \streetaddress{}
  \city{Edinburgh}
  \state{United Kingdom}
  \postcode{}
}

\author{Jean-Thomas Acquaviva}
\affiliation{%
  \institution{DDN}
  \streetaddress{}
  \city{Paris}
  \state{France}
  \postcode{}
}

\author{Anja Gerbes}
\affiliation{%
  \institution{Goethe-Universität}
  \streetaddress{}
  \city{Frankfurt am Main}
  \state{Germany}
  \postcode{}
}

\author{Lev Lafayette}
\affiliation{%
  \institution{University of Melbourne}
  \streetaddress{}
  \city{Melburne}
  \state{Australia}
  \postcode{}
}

\renewcommand{\shortauthors}{J. Kunkel et al.}

\begin{abstract}
  The HPC community has always considered the training of new and existing HPC practitioners to be of high importance to its growth.
  This diversification of HPC practitioners challenges the traditional training approaches, which are not able to satisfy the specific needs of users, often coming from non-traditionally HPC disciplines, and only interested in learning a particular set of competences.
  Challenges for HPC centres are to identify and overcome the gaps in users’ knowledge, while users struggle to identify relevant skills.

  We have developed a first version of an HPC certification program that would clearly categorize, define, and examine competences.
  Making clear what skills are required of or recommended for a competent HPC user would benefit both the HPC service providers and practitioners.
  Moreover, it would allow centres to bundle together skills that are most beneficial for specific user roles and scientific domains.
  From the perspective of content providers, existing training material can be mapped to competences allowing users to quickly identify and learn the skills they require.
  Finally, the certificates recognized by the whole HPC community simplify inter-comparison of independently offered courses and provide additional incentive for participation.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
\end{CCSXML}

\keywords{}

\maketitle

\section{Introduction}

There is a generally accepted set of skills and competencies necessary to efficiently use HPC resources.
This skill set depends on the role and domain of the practitioner but also on the available infrastructure of the center providing the computing resources.
For example, a scientist needing to run an application on a specific machine may need basic skills in Linux, MPI, environment modules, and knowledge about the batch scheduler, e.g., SLURM.
Understanding SLURM is a good example of a very fine-grained skill, indeed we can identify "resource management" as a generic skill that illustrates concepts across the rich variety of available resource managers.
Institutions which operate HPC systems typically offer regularly teaching events about general aspects of their supercomputer's hard- and software architecture and about the software environment around parallel programming and optimization.
The learning material provided by an HPC center, however, is geared to the special demands of the institutions they support and its specific HPC environment.
This content typically covers a small part of basic HPC skills which are necessary to use other HPC systems.
Moreover, they do not attest the users to have a certain competence.
Certificates are widely used in industry to attest certain knowledge but, so far, there is no similar approach for HPC training.

This lightning talk describes the current status of the certification program and the effort to create an independent body that curate the competences and issue certificates for the users.

The foundation for this work was laid with the Performance Conscious HPC (PeCoH) project, which among other goals, aims to establish an HPC certification program.
A white paper about the approach containing technical details is provided in \cite{whitepaper}.
Within the project it become quickly apparent that the local effort is useful for the wider HPC community and could be extended to a global effort.

\begin{figure*}[tb!]
	\centering
	\includegraphics[width=15.0cm]{skill-tree_top_levels.jpg}
  \vspace*{-2em}
	\caption{Top Level Competences}
	\label{f_top_level_competences}
\end{figure*}

\section{Related Work}

Relevant work can be classified into approaches to establish a curriculum or the creation of teaching material.
In academia, individual universities offer their own curriculum around scientific computing and HPC, covering theoretical aspects like the software development of numerical applications.
They are not tailored to the needs of a practitioner to actually use HPC systems effectively.
Data centers offer their own material and courses to support their own users.
Several projects address the generation and sharing of teaching material for HPC.
The EuroLab-4-HPC project establishes training in form of (online) courses\footnote{\url{https://www.eurolab4hpc.eu/}}.
The Barcelona Supercomputing Centre (BSC) aims to develop a professional training curriculum \cite{sancho2016bsc}.
The virtual organization XSEDE\footnote{\url{https://portal.xsede.org/web/xup/training/overview}} provides an online system to train the usage of an HPC system, structuring the corresponding information on their website into major topics like “Getting Started”.
The user can navigate the topics and receive further information.

\section{Certification Program}

The certification program serves two purposes:
1) the definition and organization of fine-grained competences (skills);
2) the establishment of certificates and (online) exams that confirm that users possess a certain skill.
Note that the certification program does not regulate the content -- the definition of skills and certificates is separated from content creation.
This allows the re-use of existing content but also allows to create a new ecosystem in which HPC centers or commercial companies could offer the best teaching material.
Teaching material should be marked to indicated which skills it covers.
In the future, the program may provide means to register and reference existing content of third-parties allowing users to browse the skills and navigate to teaching material.
We assume that the collaboration of scientific institutions will complement each other in producing a rich variety of content for the different learning styles.

\subsection{Skills}

The skills represent competences in a fine-grained fashion.
A skill is defined by a unique key, short name, background, level, and a description of what it encompasses.
This model can be compared to the classification of school knowledge, for example, the skill with the short name "addition" could describe the math skill of being able to add numbers successfully.
The level serves the purpose of distinguishing the expertise further, a \textit{basic level}, for example, may mean to be able to add two numbers between 1-20 while the \textit{expert level} of that skill could indicate to be able to add any numbers.

The individual skills are organized into a tree that shows generic competences close to the root and refined skills on the leafs.
The two top-levels of the skill tree are shown in \Cref{f_top_level_competences}; we have identified more than 35 skills.
In respect to the granularity, we expect the basic level of a leaf like “Bash programming” can be acquired by novel users in a workshop day.
The tree serves the purpose of navigating across the skills, and at the same time a parent node defines the scope of its children.
For example, the \textit{USE} competence provides means of using the HPC environment to perform various tasks, such as running parallel applications, using core services of the operating system.
While the tree structure has been chosen as a graphical representation, some competences are cross-referenced, particularly in the skills of the USE branch.
The tree is managed in an XML file and we offer tools to visualize the skills as mindmap or embed them into a webpage -- more information are found in \cite{whitepaper}.

\subsection{Certificates}

Certifying users with a certain competency is a core element of the program.
Since we identified so many skills, it is not useful to perform an exam on a single competence like “SLURM”.
Therefore, initially, we aim to group sets of skills into certificates and establish an online examination that attests users that they mastered a certain skill.
To be meaningful these tests must prevent cheating to some extent.
However, as any examination can be cheated with sufficient effort, we focus on practical aspects like a huge corpus of questions and some instantiated questions like \textit{how would you start ProgramX with 4 MPI processes?}

\section{Conclusions}

The HPC Certification program offers a strategy to classify and organize HPC competences.
While the idea started with the PeCoH project, we are supporting the HPC Certification Forum\footnote{\url{https://hpc-certification.org}} which is an independent international body that aims to sustain the work.
The certification forum has the role of a (virtual) central authority to curate and maintain the skill tree and certificates.
Moreover, the forum supports tools and an ecosystem around the competences.

\appendix

\begin{acks}
\small
This work was supported by the German Research Foundation (DFG) under grants LU 1353/12-1, OL 241/2-1, and RI 1068/7-1.
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

\end{document}

### 2019-04-11 paper.tex
Further

@@
 \usepackage{cleveref}
-
+\usepackage{todonotes}
 \usepackage{graphicx}
@@
 \DeclareGraphicsExtensions{.png,.pdf,.jpg,.jpeg}
+
+\newcommand{\jk}[1]{\todo[inline]{TODO: #1}}
 
@@
 
-This lightning talk describes the current status of the certification program and the effort to create an independent body that curate the competences and issue certificates for the users.
+This article describes the current status of the certification program by looking back for the one year of this independent body that curate the competences and aims to issue certificates for the users.
 
-The foundation for this work was laid with the Performance Conscious HPC (PeCoH) project, which among other goals, aims to establish an HPC certification program.
-A white paper about the approach containing technical details is provided in \cite{whitepaper}.
-Within the project it become quickly apparent that the local effort is useful for the wider HPC community and could be extended to a global effort.
+Our previous work described the evolution from the bootstraping project towards the independent body of the HPC Certification forum \cite{TAHCPKHHSS19}.
 
@@
 \section{Related Work}
+\jk{Please everyone!}
 
@@
 While the tree structure has been chosen as a graphical representation, some competences are cross-referenced, particularly in the skills of the USE branch.
-The tree is managed in an XML file and we offer tools to visualize the skills as mindmap or embed them into a webpage -- more information are found in \cite{whitepaper}.
+The tree is managed in an XML file and we offer tools to visualize the skills as mindmap or embed them into a webpage.
 

### 2019-04-11 paper.tex
New structure

@@
 
-  We have developed a first version of an HPC certification program that would clearly categorize, define, and examine competences.
-  Making clear what skills are required of or recommended for a competent HPC user would benefit both the HPC service providers and practitioners.
-  Moreover, it would allow centres to bundle together skills that are most beneficial for specific user roles and scientific domains.
-  From the perspective of content providers, existing training material can be mapped to competences allowing users to quickly identify and learn the skills they require.
-  Finally, the certificates recognized by the whole HPC community simplify inter-comparison of independently offered courses and provide additional incentive for participation.
+  With the HPC Certification Forum we aim to clearly categorize, define, and examine competences which brings benefit to all stakeholders involved in training.
+  In this paper, we report the status and progress this independent body has made during the first year of its existence.
+  Particularly, in various directions drafts of processes and prototypes have been generated to create a holistic ecosystem that will mature over this year.
 \end{abstract}
@@
 This article describes the current status of the certification program by looking back for the one year of this independent body that curate the competences and aims to issue certificates for the users.
+Our previous work described the evolution from the project that sparked the initial activity that lead to the independent body of the HPC Certification forum \cite{TAHCPKHHSS19}.
 
-Our previous work described the evolution from the bootstraping project towards the independent body of the HPC Certification forum \cite{TAHCPKHHSS19}.
+\section{The HPC Certification Forum}
+
+\section{Skill Organization}
+
+\subsection{Skill Example}
+
+\section{Certification}
+
+\subsection{Certificates}
+
+\subsection{Examination Process}
+
+\section{Ecosystem}
+
+\subsection{Linking Training Material}
+
+\subsection{Supportive Tools}
+
+\section{Discussion of the Benefits}
+
+Making clear what skills are required of or recommended for a competent HPC user would benefit both the HPC service providers and practitioners.
+Moreover, it would allow centres to bundle together skills that are most beneficial for specific user roles and scientific domains.
+From the perspective of content providers, existing training material can be mapped to competences allowing users to quickly identify and learn the skills they require.
+Finally, the certificates recognized by the whole HPC community simplify inter-comparison of independently offered courses and provide additional incentive for participation.
+
+\section{Conclusion}
 

### 2019-04-11 paper.tex
Skill tree update

@@
 
-This article describes the current status of the certification program by looking back for the one year of this independent body that curate the competences and aims to issue certificates for the users.
-Our previous work described the evolution from the project that sparked the initial activity that lead to the independent body of the HPC Certification forum \cite{TAHCPKHHSS19}.
+This article describes the current status of the certification program offered by the HPC Certification Forum by looking back for the one year of this independent body that curate the competences and aims to issue certificates for the users.
+Our previous work described the evolution from the project that sparked the initial activity that lead to the independent body of the HPC Certification Forum \cite{TAHCPKHHSS19}.
 
 \section{The HPC Certification Forum}
+
+The HPC Certification Forum (HPCCF) has the role of a (virtual) central authority to curate and maintain a skill tree of competences, the creation of certificates, and examination of practitioners to attest certificates.
+Moreover, the forum supports tools and an ecosystem around the competences.
+
+\jk{Integrate}
+
+1) the definition and organization of fine-grained competences (skills);
+2) the establishment of certificates and (online) exams that confirm that users possess a certain skill.
+Note that the certification program does not regulate the content -- the definition of skills and certificates is separated from content creation.
+This allows the re-use of existing content but also allows to create a new ecosystem in which HPC centers or commercial companies could offer the best teaching material.
+Teaching material should be marked to indicated which skills it covers.
+In the future, the program may provide means to register and reference existing content of third-parties allowing users to browse the skills and navigate to teaching material.
+We assume that the collaboration of scientific institutions will complement each other in producing a rich variety of content for the different learning styles.
 
@@
 
-\section{Conclusion}
-
-\begin{figure*}[tb!]
-	\centering
-	\includegraphics[width=15.0cm]{skill-tree_top_levels.jpg}
-  \vspace*{-2em}
-	\caption{Top Level Competences}
-	\label{f_top_level_competences}
-\end{figure*}
-
 \section{Related Work}
@@
 
-\section{Certification Program}
+\section{Conclusion}
 
-The certification program serves two purposes:
-1) the definition and organization of fine-grained competences (skills);
-2) the establishment of certificates and (online) exams that confirm that users possess a certain skill.
-Note that the certification program does not regulate the content -- the definition of skills and certificates is separated from content creation.
-This allows the re-use of existing content but also allows to create a new ecosystem in which HPC centers or commercial companies could offer the best teaching material.
-Teaching material should be marked to indicated which skills it covers.
-In the future, the program may provide means to register and reference existing content of third-parties allowing users to browse the skills and navigate to teaching material.
-We assume that the collaboration of scientific institutions will complement each other in producing a rich variety of content for the different learning styles.
+\begin{figure*}[tb!]
+	\centering
+	\includegraphics[width=15.0cm]{skill-tree}
+	\caption{Top Level Competences with an expansion of PE4}
+	\label{f_top_level_competences}
+\end{figure*}
+
+\jk{Old stuff}
 
@@
 
-\section{Conclusions}
-
-The HPC Certification program offers a strategy to classify and organize HPC competences.
-While the idea started with the PeCoH project, we are supporting the HPC Certification Forum\footnote{\url{https://hpc-certification.org}} which is an independent international body that aims to sustain the work.
-The certification forum has the role of a (virtual) central authority to curate and maintain the skill tree and certificates.
-Moreover, the forum supports tools and an ecosystem around the competences.
-
 \appendix

### 2019-04-12 paper.tex
Further

@@
 \begin{document}
-\title{Looking Back: One Year HPC Certification Forum}
+\title{One Year HPC Certification Forum in Retrospective}
 
@@
 
+The competences are organized in a tree that serves the purpose to organize and structure the skills from a coarse-grained to a fine-grained representation allowing users to browse the skill based on the semantics.
+The root level of our current skill tree is shown in \Cref{skill-tree}.
+The idea is that the skills from the root level provide an indication about their scope,
+e.g., are they core knowledge, dealing with the usage of HPC environments, or about programming.
+This should allow the user to rapidly drill into the skill representation.
+On the leaf level, a skill is fine-grained -- we scope the level of detail here to be able to be taught in a 1.5 hour lecture up to a 4 hour workshop.
+
+As the tree serves the purpose to organize the skills, there can also be references from one branch to a skill in another.
+This import allows to reuse the definitions of the skills while still allowing users to navigate the tree according to the semantics.
+
+\begin{figure*}[tb!]
+	\centering
+	\includegraphics[width=15.0cm]{skill-tree}
+	\caption{Top Level Competences with an expansion of PE4}
+	\label{f_top_level_competences}
+\end{figure*}
+
+\subsection{Description of a skill}
+
+Each skill on the tree and even the inner nodes are described in more detail as follows:
+
+\begin{itemize}
+  \item \textbf{ID}: ID according the organization in the skill tree.
+  \item \textbf{Name}: A speaking name for a skill.
+  \item \textbf{Background}: Provides brief information motivating the need for the skill and how this skill fits into the skill map; what is the bigger picture.
+  \item \textbf{Aims}:
+  \jk{TODO}
+  Programme or module aims serve as broad purposes or goals and are generally a statement of the intentions of the teacher or school when designing or running the course.
+They are not intended to be statements of what students will learn or do, but rather over-arching intentions of the course.
+At a basic level, aims are trying to answer two questions: What is the purpose of this programme or module?
+What is the programme or module trying to achieve?
+reference
+  \item \textbf{Learning outcomes}: Defines briefly what what practitioners know / will learn. The objected are statements what prospect learners are able to do, they should
+  describe or define an action be clearly stated be measurable/quantifiable to some extent, for example, by using action words.
+\end{itemize}
+
+The closer a skill is to the root, the more abstract it is defined, while leaf nodes cover the knowledge for the specific skill.
+
 \subsection{Skill Example}
+
+The following skill describes a leaf-node for SLURM, note that it is expected to complement a generic skill that describes how the general workload management works in HPC.
+
+\begin{itemize}
+  \item \textbf{ID}: USE4.2.2-B
+  \item \textbf{Name}: SLURM Workload manager
+  \item \textbf{Background}: SLURM is a widely used open-source workload manager providing various advanced features.
+  \item \textbf{Aims}:
+  \begin{itemize}
+    \item To enable practitioners to comprehend and describe the basic architecture of SLURM and the suite of tools.
+    \item To use relevant tools to run and monitor (parallel) applications
+  \end{itemize}
+  \item \textbf{Learning outcomes}:
+  \begin{itemize}
+  \item run interactive jobs with salloc, a batch job with sbatch
+  \item explain the architecture of SLURM, i.e., the role of slurmd, srun and the injection of environment variables
+  \item explain the function of the tools: sacct, sbatch, salloc, srun, scancel, squeue, sinfo
+  \item explain time limits and the benefit of a backfill scheduler
+  \item comprehend that environment variables are set when running a job
+  \item comprehend and describe the expected behavior of a simple job scripts
+  \item comprehend how variables are prioritized when using command line and a script
+  \item change a provided job template and embed them into shell scripts to run a variety of parallel applications
+  \item analyze the output generated from submitting to the job scheduler and typically generated errors
+  \end{itemize}
+\end{itemize}
+
+%\begin{itemize}
+%  \item \textbf{Name}:
+%  \item \textbf{Background}:
+%  \item \textbf{Aim}:
+%  \item \textbf{Learning outcomes}:
+%\end{itemize}
 
@@
 \section{Conclusion}
-
-\begin{figure*}[tb!]
-	\centering
-	\includegraphics[width=15.0cm]{skill-tree}
-	\caption{Top Level Competences with an expansion of PE4}
-	\label{f_top_level_competences}
-\end{figure*}
 

### 2019-04-12 paper.tex
Skill organization

@@
 This should allow the user to rapidly drill into the skill representation.
-On the leaf level, a skill is fine-grained -- we scope the level of detail here to be able to be taught in a 1.5 hour lecture up to a 4 hour workshop.
+The closer a skill is to the root, the more abstract it is defined, while leaf nodes cover the knowledge for the specific skill.
+
+Within a single skill, there can also be multiple levels (basic, intermediate, expert level) building upon each other -- thus, we expect that practitioners acquire the lower levels before progressing to more complex levels.
+The basic level should cover the most relevant aspect of the skill, i.e., needed by anyone that uses the skill, the intermediate level (used for common exceptional cases) and expert levels (used in special circumstances)  are needed only for a subset of users.
+Typically, an institution has only few experts (if one at all).
 
@@
 \begin{itemize}
-  \item \textbf{ID}: ID according the organization in the skill tree.
-  \item \textbf{Name}: A speaking name for a skill.
-  \item \textbf{Background}: Provides brief information motivating the need for the skill and how this skill fits into the skill map; what is the bigger picture.
-  \item \textbf{Aims}:
-  \jk{TODO}
-  Programme or module aims serve as broad purposes or goals and are generally a statement of the intentions of the teacher or school when designing or running the course.
-They are not intended to be statements of what students will learn or do, but rather over-arching intentions of the course.
-At a basic level, aims are trying to answer two questions: What is the purpose of this programme or module?
-What is the programme or module trying to achieve?
-reference
-  \item \textbf{Learning outcomes}: Defines briefly what what practitioners know / will learn. The objected are statements what prospect learners are able to do, they should
-  describe or define an action be clearly stated be measurable/quantifiable to some extent, for example, by using action words.
+  \item \textbf{ID}: ID according the organization in the skill tree. The last character indicates the level of the skill (Basic, Intermediate, or Advanced).
+  \item \textbf{Name}: A speaking name for the skill.
+  \item \textbf{Background}: Provides brief information motivating the need for the skill and how this skill fits into the skill tree; what is the bigger picture.
+  \item \textbf{Aims}\footnote{The definition of aims and outcomes follows literature for higher education \cite{williamson2011good} and \url{https://www.heacademy.ac.uk/system/files/assessment-learning-outcomes.pdf}.}: They serve as broad purposes and are generally a statement of the intentions of the skill.
+  They are not the statements of what a practitioner will learn or do.
+  At a basic level, aims are trying to answer two questions: What is the purpose of this skill?
+  What is the skill trying to achieve?
+  \item \textbf{Learning outcomes (LOs)}: Defines briefly what what practitioners will know and learn.
+  The objected are statements what prospect learners are able to do, they should
+  describe or define an action be clearly stated be measurable/quantifiable to some extent by using action words.
 \end{itemize}
 
-The closer a skill is to the root, the more abstract it is defined, while leaf nodes cover the knowledge for the specific skill.
+On the leaf level, a skill is fine-grained and orthogonal to other skills -- we scope the level of detail here to be able to be taught in a 1.5 hour lecture up to a 4 hour workshop.
+We believe this is a good granularity as it allows practitioners to cherry-pick the relevant skills and lecturers and examiners to prepare small lectures with well-defined content.
+For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that provide the foundation to many specialized skills each representing a specific hardware or software technology.
 
-\subsection{Skill Example}
+The aggregation within the tree is similar to the aggregation found in education as part of “individual teaching events”, “those specified for modules or short courses”, and “those specified for whole degree programmes” \cite{hussey2008learning}.
+While that Hussey et al.
+conclude that LOs on the coarse grained level are not useful for high-level education, we use a similar concept, but relax the granularity/abstraction level of the learning outcome.
 
-The following skill describes a leaf-node for SLURM, note that it is expected to complement a generic skill that describes how the general workload management works in HPC.
+\subsection{Skill Examples}
+
+Next, we present a generic skill that describes an inner-node in more details.
+There is no actual delivery as a module or teaching event to deliver the content, it serves the purpose to inform the practitioner about the importance of the skill.
+
+\begin{itemize}
+  \item \textbf{ID}: USE4.2-B
+  \item \textbf{Name}: Executing parallel applications
+  \item \textbf{Background}:
+  Parallel computers are operated differently than a normal PC, all users must share the system.
+Therefore, various operative procedures are in place.
+Users must understand these concepts and procedures to be able to use the available resources of a system to run a parallel application.
+Moreover, individual solutions can often be found in a specific system.
+  \item \textbf{Aim}: To enable practitioners to comprehend the concepts and procedures for running parallel applications in HPC environments.
+  To use the system to run and monitor the execution of parallel applications on the HPC system.
+
+  \item \textbf{Learning outcomes}:
+    \begin{itemize}
+    \item explain the concepts and procedures for resource allocation and job execution in an HPC environment
+    \item run interactive jobs and batch jobs
+    \item comprehend and describe the expected behavior of job scripts
+    \item change provided job scripts and embed them into shell scripts to run a variety of parallel applications
+    \item analyze the output generated from a job scheduler and describe the cause of typically generated errors
+    \end{itemize}
+\end{itemize}
+
+The next leaf-level skill describes how workload management works in general in HPC regardless of the specific software that implements such concepts.
+It is intended that the aim and outcomes from the parent skill above are covered to some extend and refined into specifics.
+
+\begin{itemize}
+  \item \textbf{ID}: USE4.2.1-B
+  \item \textbf{Name}: Workload manager introduction
+  \item \textbf{Background}: There is a wide range of different workload managers in use. This skill covers generic and widely used concepts.
+  \item \textbf{Aim}: To enable practitioners to comprehend and describe the basic architecture and concepts of resource allocation for an HPC system.
+  \item \textbf{Learning outcomes}:
+
+  \begin{itemize}
+  \item comprehend the exclusive and shared usage model in HPC
+  \item differentiate batch and interactive job submission
+  \item comprehend the generic concepts and architecture of resource manager, scheduler, job and job script
+  \item explain the role of environment variables as a means to communicate
+  \item comprehend accounting principles
+  \item explain the generic steps to run and monitor a single job
+  \end{itemize}
+\end{itemize}
+
+The following skill describes a leaf-level skill for the usage of SLURM in the basic level.
+While there is no formal dependency to the introduction (skill USE4.2.2-B), it is expected that practitioners have obtained the other skill before learning this one.
 
@@
   \begin{itemize}
+    \item To enable practitioners to use relevant tools to run and monitor parallel applications using SLURM.
     \item To enable practitioners to comprehend and describe the basic architecture of SLURM and the suite of tools.
-    \item To use relevant tools to run and monitor (parallel) applications
   \end{itemize}
@@
 
+As you can see from the definition of the skill, these learning outcomes are focusing on the core needs to actually use SLURM effectively.
+An intermediate skill could, e.g., add reservations.
+
 %\begin{itemize}
+%  \item \textbf{ID}:
 %  \item \textbf{Name}:
@@
 \subsection{Examination Process}
+
+A benefit of the fine-grained definition of learning outcomes is
 

### 2019-04-13 paper.tex
Further

@@
 Moreover, the forum supports tools and an ecosystem around the competences.
+
+HPC Certification Program
 
@@
 
+The certification
+
+\begin{verbatim}
+-----BEGIN PGP SIGNED MESSAGE-----
+Hash: SHA512
+HPC Certification Forum Certificate
+This text confirms that "Julian M. Kunkel" has
+successfully obtained the certificate
+"The basic certificate" (id: 4711) at 02/2019.
+Verification URL: https://hpc-certification.org/[...]
+-----BEGIN PGP SIGNATURE-----
+[...]
+-----END PGP SIGNATURE-----
+\end{verbatim}
+
+\Cref{fig:awardedCertificate}
+
+\begin{figure}
+  \includegraphics[width=0.48\textwidth]{JulianMKunkel}
+  \caption{Draft for an awarded certificate}
+  \label{fig:awardedCertificate}
+\end{figure}
+
 \subsection{Certificates}
@@
 
-\subsection{Linking Training Material}
+\section{Training Delivery}
+
+The HPC Certification Forum is not developing training material directly or competing with providers of training material.
+However, we support individuals and institutions by endorsing and promoting their training materials and courses in two ways.
+
+Firstly, an author of training material is allowed to indicate on the training material itself or on promotional material the fact
+which skills are covered by the material completely or partially.
+We provide a seal that can be used for that purpose (see \Cref{fig:seal-teaching}).
+The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material
+registers a link to the material or course and their email address on our webpage using an online form.
+That way, the HPCCF is informed about the usage of the seal.
+
+Secondly, we will link on our webpage the endorsed training material for the individual skills and certificates.
+By using JavaScript and dynamic webpage we will provide various views on the skills with and without links to suitable training materials.
+
+Note that we are not intending to verify the correct usage of the skill explicitly.
+However, in case the training material or course doesn't deliver the expected material practitioners may complain and we will remove the training material from our webpage.
+
+We expect that this strategy will lead to the availability of good free training material for most skills
+while companies and individuals can still charge for effective training courses.
+
+\begin{figure}
+  \includegraphics[width=0.3\textwidth]{certified}
+  \caption{Draft for the seal for teaching material}
+  \label{fig:seal-teaching}
+\end{figure}
 

### 2019-04-13 paper.tex
Examination process.

@@
 
-The certification
+A certificate shall attest a user the expertise in the covered skills.
+Ensuring the integrity of a certificate is an important aspect, i.e., we must check that the learning outcomes of the covered skills are achieved and prevent self-cheating or dishonesty.
 
+Students can always cheat an examination -- the risk depends on the type of exam and methods used for the assessment.
+As we want to enable a cost-effective assessment (free for the practitioner), we chose an online examination.
+This increases the opportunity for cheating \cite{rowe2004cheating} but we deploy several  strategies that aim to minimize the risk of self-cheating as raising awareness, a question pool, and delay.
+Since knowledge can age, the month and year an examination took place is also indicated.
+As certificates bundle multiple skills together as examination of a single fine-grained leaf-level skill would be too easy for short-term memorization and prone to self-cheating.
+We believe the incentive to deliberately fake the assessment, e.g., by having the exam filled by someone else, and thus, being awarded a certificate is low.
+Therefore, we address this only in a lightweight fashion.
+
+We discuss the prototypical process that we implemented for the examination in the following.
+
+\subsection{Examination Process}
+
+The examination can be started by users any time but upon submission a delay is employed.
+Firstly, a user has to register for the examination using name and email address and optional affiliation.
+On the webpage, the process is explained, together with privacy policies.
+Further, a paragraph provides the integrity policy defining cheating and encouraging honesty.
+Practitioners are asked to opt-in the policy statement.
+With the registration, we generate an encrypted token on the server that is returned to the user by email.
+At this stage, we do not store any information about the user on the server.
+
+The email contains a link that will start the examination.
+The user chooses to start the examination by clicking on the link; then the information about the user and the time of starting the examination is stored in a temporary database.
+
+The summative assessment itself is conducting using multiple choice questions.
+Therefore, for each skill, we will be developing a pool of questions but also allow contribution of questions.
+A question has more possible answers (e.g., 10) -- the practitioner has to select if each  statement is true or false.
+An examination consists of randomly selected questions and five answers per question are selected.
+
+Once the user submits the exam results, all selected answers are stored on the server for validation -- which is done manually at the moment.
+If the user meets the criteria to pass (typically 70\% correct selection), a certificate is issued and send to the user by email.
+We then delete all personal information about the user from the server but preserve the affiliation and the raw responses.
+The affiliation is used for promotion purposes while the raw responses will be analyzed to optimize the questions.
+For example, when we identify that most users make a particular mistake, this may be an indication that the question or answer is ambivalent and needs to be improved.
+
+If the user didn't meet the criteria to pass, we will inform him about the rough score obtained.
+The user can retry to obtain the certificate after a cooldown period (typically one week) but not immediately to prevent success via brute force methods.
+To enforce this, we keep the information about the date the exam was conducted linked to his name and email.
+
+As the sole purpose of the multiple choice questions is the examination, we will not reveal which questions are answered correctly.
+We assume that high quality training material for individual skills will offer multiple choice questions that serve the purpose of feedback which promotes learning  \cite{epstein2002immediate}.
+
+\subsection{Certificates}
+
+Upon successful assessment, a certificate is awarded, it consists of two parts:
+A PDF with the key information needed for a meaningful certificate (for a draft, see \Cref{fig:awardedCertificate}).
+The name and identifier for the certificate is found in the center and below (here 4711 and “the basic certificate”).
+
+Secondly, a text file is given to the user that provides the same information.
+It is PGP signed using the private key of the HPC Certification Forum to allow verification with the published public key.
+It also contains a verification URL that can be given to a third-party allowing verification of the information.
+
+The file looks as follows:
 \begin{verbatim}
@@
 
-\Cref{fig:awardedCertificate}
-
 \begin{figure}
@@
 
-\subsection{Certificates}
-
-\subsection{Examination Process}
-
-A benefit of the fine-grained definition of learning outcomes is
-
 \section{Ecosystem}
 
-\section{Training Delivery}
+\subsection{Training Delivery}
 

### 2019-04-13 paper.tex
Shifting stuff around

@@
   With the HPC Certification Forum we aim to clearly categorize, define, and examine competences which brings benefit to all stakeholders involved in training.
-  In this paper, we report the status and progress this independent body has made during the first year of its existence.
-  Particularly, in various directions drafts of processes and prototypes have been generated to create a holistic ecosystem that will mature over this year.
+  In this article, we report the status and progress this independent body has made during the first year of its existence: processes and prototypes have been drafted that will  mature to a holistic ecosystem beneficial for all stackholders in HPC education.
 \end{abstract}
@@
 For example, a scientist needing to run an application on a specific machine may need basic skills in Linux, MPI, environment modules, and knowledge about the batch scheduler, e.g., SLURM.
-Understanding SLURM is a good example of a very fine-grained skill, indeed we can identify "resource management" as a generic skill that illustrates concepts across the rich variety of available resource managers.
+Understanding SLURM is a good example of a very fine-grained skill, indeed we can identify “resource management” as a generic skill that illustrates concepts across the rich variety of available resource managers.
 Institutions which operate HPC systems typically offer regularly teaching events about general aspects of their supercomputer's hard- and software architecture and about the software environment around parallel programming and optimization.
@@
 
-This article describes the current status of the certification program offered by the HPC Certification Forum by looking back for the one year of this independent body that curate the competences and aims to issue certificates for the users.
-Our previous work described the evolution from the project that sparked the initial activity that lead to the independent body of the HPC Certification Forum \cite{TAHCPKHHSS19}.
+This article describes the current status of the certification program offered by the HPC Certification Forum.
+Our previous work provided a brief overview of the evolution from the project that sparked  the HPC Certification Forum \cite{TAHCPKHHSS19} while this article provides details highlighting mechanisms and design decisions.
+
+The article is structured as follows:
+First, we introduce the HPC Certification Forum and the program in \Cref{sec:forum}.
+Then, an overview of the status is given in \Cref{sec:status}.
+Next, the organization of competences is discussed in \Cref{sec:skills}.
+This leads to the prototypical approach for the certification process in \Cref{sec:certification}.
+Related work is presented in \Cref{sec:related}.
+Finally, the article is concluded in \Cref{sec:conclusion}.
 
 \section{The HPC Certification Forum}
+\label{sec:forum}
 
-The HPC Certification Forum (HPCCF) has the role of a (virtual) central authority to curate and maintain a skill tree of competences, the creation of certificates, and examination of practitioners to attest certificates.
+The HPC Certification Forum (HPCCF) has the role of a (virtual) central authority to curate and maintain a certification program.
+The program consists of the definition of competences, the creation of certificates, and the examination of practitioners to attest that they possess certain competences.
 Moreover, the forum supports tools and an ecosystem around the competences.
 
-HPC Certification Program
+The HPCCF aims to support existing activities and complements them by providing a unified and clear way of mapping out the relevant HPC competences for practitioners.
+Thus, the HPCCF does not regulate the content of training material; we purposely separate the definition of skills and certificates with their examinations from content delivery.
+Similarly, the program does not prescribe a curriculum or any fixed order by which skills need to be obtained.
 
-\jk{Integrate}
+The forum is organized using a Webpage\footnote{http://hpc-certification.org} and utilizes Slack for communication and monthly meetings.
+Members are organized in different roles:
+Anyone can become an associate member in the HPCCF free of charge -- e.g., observing the status, being listed on the webpage.
+Full members must actively contribute to the program to some extent and have voting rights for the roles of the steering board.
+The steering board directs the overall activities and is organized in different responsibilities, i.e., into topic-specific chairs.
 
-1) the definition and organization of fine-grained competences (skills);
-2) the establishment of certificates and (online) exams that confirm that users possess a certain skill.
-Note that the certification program does not regulate the content -- the definition of skills and certificates is separated from content creation.
-This allows the re-use of existing content but also allows to create a new ecosystem in which HPC centers or commercial companies could offer the best teaching material.
-Teaching material should be marked to indicated which skills it covers.
-In the future, the program may provide means to register and reference existing content of third-parties allowing users to browse the skills and navigate to teaching material.
-We assume that the collaboration of scientific institutions will complement each other in producing a rich variety of content for the different learning styles.
+\section{Status of the Activities}
+\label{sec:status}
 
-\section{Skill Organization}
+\begin{itemize}
+  \item Technical representation of skills as Markdown and editable on a Wiki
+  \item A prototype process for the certification addressing privacy issues
+  \item Tools to generate and conduct an online multiple-choice examination
+  \item 
+\end{itemize}
 
-The competences are organized in a tree that serves the purpose to organize and structure the skills from a coarse-grained to a fine-grained representation allowing users to browse the skill based on the semantics.
+\section{Skills}
+\label{sec:skills}
+
+A skill is defined as a set of competences (learning outcomes) and some metadata.
+This model can be compared to the classification of school knowledge, for example, the skill with the short name “addition” could describe the math skill of being able to add numbers successfully.
+Within a single skill, there can also be multiple levels (basic, intermediate, expert level) building upon each other that distinguish the expertise further.
+We expect that practitioners acquire the lower levels before progressing to more complex levels.
+In our addition example, \textit{basic level}, for example, may mean to be able to add two positive numbers while the \textit{expert level} of that skill could indicate to be able to add multiple numbers.
+
+The basic level should cover the most relevant aspect of the skill, i.e., needed by anyone that uses the skill, the intermediate level (used for common exceptional cases) and expert levels (used in special circumstances)  are needed only for a subset of users.
+Typically, an institution has only few experts (if one at all).
+
+The skills are organized in a tree that serves the purpose to organize and structure the skills from a coarse-grained to a fine-grained representation allowing users to browse the skill based on the semantics.
 The root level of our current skill tree is shown in \Cref{skill-tree}.
@@
 The closer a skill is to the root, the more abstract it is defined, while leaf nodes cover the knowledge for the specific skill.
-
-Within a single skill, there can also be multiple levels (basic, intermediate, expert level) building upon each other -- thus, we expect that practitioners acquire the lower levels before progressing to more complex levels.
-The basic level should cover the most relevant aspect of the skill, i.e., needed by anyone that uses the skill, the intermediate level (used for common exceptional cases) and expert levels (used in special circumstances)  are needed only for a subset of users.
-Typically, an institution has only few experts (if one at all).
 
@@
 \section{Certification}
+\label{sec:certification}
 
@@
 \section{Ecosystem}
+\label{sec:ecosystem}
+
+We encourage the development of an ecosystem around the HPC classification, we are supporting training and tool development.
 
@@
 
-We expect that this strategy will lead to the availability of good free training material for most skills
-while companies and individuals can still charge for effective training courses.
+We expect that this strategy will lead to the availability of good free training material for most skills while companies and individuals can still charge for effective training courses.
+Ultimately, the resulting training material will complement each other leading to a rich variety of content suitable for each individual practitioner, e.g., addressing different learning styles and languages.
 
@@
 
-\section{Discussion of the Benefits}
+\section{Related Work}
 
-Making clear what skills are required of or recommended for a competent HPC user would benefit both the HPC service providers and practitioners.
-Moreover, it would allow centres to bundle together skills that are most beneficial for specific user roles and scientific domains.
-From the perspective of content providers, existing training material can be mapped to competences allowing users to quickly identify and learn the skills they require.
-Finally, the certificates recognized by the whole HPC community simplify inter-comparison of independently offered courses and provide additional incentive for participation.
+\label{sec:related}
 
-\section{Related Work}
 \jk{Please everyone!}
@@
 \section{Conclusion}
+\label{sec:conclusion}
 
-\jk{Old stuff}
+This allows the re-use of existing content but also allows to create a new ecosystem in which HPC centers or commercial companies could offer the best teaching material.
+Teaching material should be marked to indicated which skills it covers.
+In the future, the program may provide means to register and reference existing content of third-parties allowing users to browse the skills and navigate to teaching material.
 
-\subsection{Skills}
+\subsection{Benefits}
 
-The skills represent competences in a fine-grained fashion.
-A skill is defined by a unique key, short name, background, level, and a description of what it encompasses.
-This model can be compared to the classification of school knowledge, for example, the skill with the short name "addition" could describe the math skill of being able to add numbers successfully.
-The level serves the purpose of distinguishing the expertise further, a \textit{basic level}, for example, may mean to be able to add two numbers between 1-20 while the \textit{expert level} of that skill could indicate to be able to add any numbers.
+HPC practitioners
+Increase motivation to participate
+(Certificates are recognized in CV)
+Validate knowledge via tests
+Browse of relevant competences
+Identify recommended and required skills
+Compare teaching offers across sites
+Data centers
 
-The individual skills are organized into a tree that shows generic competences close to the root and refined skills on the leafs.
-The two top-levels of the skill tree are shown in \Cref{f_top_level_competences}; we have identified more than 35 skills.
-In respect to the granularity, we expect the basic level of a leaf like “Bash programming” can be acquired by novel users in a workshop day.
-The tree serves the purpose of navigating across the skills, and at the same time a parent node defines the scope of its children.
-For example, the \textit{USE} competence provides means of using the HPC environment to perform various tasks, such as running parallel applications, using core services of the operating system.
-While the tree structure has been chosen as a graphical representation, some competences are cross-referenced, particularly in the skills of the USE branch.
-The tree is managed in an XML file and we offer tools to visualize the skills as mindmap or embed them into a webpage.
+Increase sharing of teaching materials
+Documentation of taught skills simplified
+Identify missing teaching activities
+Tailor skill-tree specifically to users
+Correlate lack of skills with efficient us
 
-\subsection{Certificates}
-
-Certifying users with a certain competency is a core element of the program.
-Since we identified so many skills, it is not useful to perform an exam on a single competence like “SLURM”.
-Therefore, initially, we aim to group sets of skills into certificates and establish an online examination that attests users that they mastered a certain skill.
-To be meaningful these tests must prevent cheating to some extent.
-However, as any examination can be cheated with sufficient effort, we focus on practical aspects like a huge corpus of questions and some instantiated questions like \textit{how would you start ProgramX with 4 MPI processes?}
+Making clear what skills are required of or recommended for a competent HPC user would benefit both the HPC service providers and practitioners.
+Moreover, it would allow centres to bundle together skills that are most beneficial for specific user roles and scientific domains.
+From the perspective of content providers, existing training material can be mapped to competences allowing users to quickly identify and learn the skills they require.
+Finally, the certificates recognized by the whole HPC community simplify inter-comparison of independently offered courses and provide additional incentive for participation.
 

### 2019-04-13 paper.tex
So far...

@@
 
-\section{Status of the Activities}
+\section{Overview of the Activities}
 \label{sec:status}
 
-\begin{itemize}
-  \item Technical representation of skills as Markdown and editable on a Wiki
-  \item A prototype process for the certification addressing privacy issues
-  \item Tools to generate and conduct an online multiple-choice examination
-  \item 
-\end{itemize}
+During the first year of the existence of the HPCCF, the discussion within the forum and with partners has lead to the establishment of various processes and prototypes for technical tools that are described in the following briefly.
+Further details of the overview are provided in subsequent sections.
+
+\paragraph{Management}
+At ISC-HPC 2018, the first steering board had been elected.
+We established communication channels via webpage, email and Slack for regular discussion.
+Slack is also used to conduct our monthly open meetings between members and the steering board.
+At beginning we used video conferencing tools, but found that the chat provides a more inclusive discussion and the asynchronous nature is more productive.
+We also established relations with various stackholders involved in HPC education growing the participation in the forum.
+Meeting notes with action items are extracted from Slack and documented using Google Doc.
+
+Note that until now contributions of members are voluntarily and follow the schedule as agreed between the contributor and the HPCCF board.
+We manage the prospect contributions in a Trello board; each member can manage its own card.
+
+\paragraph{Technical}
+According to our goals, we address 1) the definition of competences; 2) the creation of certificates; 3) the examination of practitioners; and 4) an ecosystem of tools supporting them.
+
+For all these sub-goals we made substantial progress.
+While the definition and organization of competences was the main focus, we prototyped various tools and processes that embed the competences into the wider education ecosystem.
+
+Firstly, we finalized the templates for the description of a competence considering pedagogic literature from higher education.
+We are still working on mapping out all relevant competences, but included also new topics that will be covered in the first version of the certification program.
+
+The definition of the competences covered by the program is version controlled with Git.
+The competences are available in XML and Markdown format.
+A Wiki allows to edit the competences and simplifies access for non-technical users.
+A navigable JavaScript representation of the skill tree is available that can be customized for the HPCCF but also for end-users.
+
+Prototypical processes and tools have been developed and deployed for curation of the examination questions and for conducting an online multiple-choice examination.
 
@@
 The skills are organized in a tree that serves the purpose to organize and structure the skills from a coarse-grained to a fine-grained representation allowing users to browse the skill based on the semantics.
-The root level of our current skill tree is shown in \Cref{skill-tree}.
-The idea is that the skills from the root level provide an indication about their scope,
-e.g., are they core knowledge, dealing with the usage of HPC environments, or about programming.
+The root level of our current skill tree is shown in \Cref{fig:skill-tree}; we aim to finalize the tree this year.
+The basic idea is that the skills from the root level enable navigation by providing an indication about their scope, e.g., are they core knowledge, dealing with the usage of HPC environments, or about programming.
 This should allow the user to rapidly drill into the skill representation.
@@
 	\includegraphics[width=15.0cm]{skill-tree}
-	\caption{Top Level Competences with an expansion of PE4}
-	\label{f_top_level_competences}
+	\caption{Skill tree top level competences with an expansion of PE4}
+	\label{fig:skill-tree}
 \end{figure*}
@@
 
-We discuss the prototypical process that we implemented for the examination in the following.
+A process has also been created for prospect contributors of examination questions.
+The questions are the only proprietary component for the HPCCF using restrictive license terms for authors while we give credit to them.
+We considered this necessary to minimize the establishment of solution databases; we omit further details here.
+
+We discuss the prototypical process that we implemented for conducting examination in the following.
 
@@
 
-\subsection{Supportive Tools}
+\subsection{Navigation}
+%\paragraph{Navigation}
+Thanks to the contributions of the PeCoH project, a JavaScript prototype enables the embedding of a navigable skill tree into a webpage.
+The script can be used by different stackholders to present their own view on the skill-tree.
+By view we mean the selection and organization of the skills, and the additional information provided when navigating the tree.
+For instance, you could have a tree for a specific scientific domain, for a specific data center, or even for the role of the tester of a specific application; it could indicate which skills are mandatory or beneficial for these use cases, providing links to training material or adding further supplementary information.
 
@@
 \small
-This work was supported by the German Research Foundation (DFG) under grants LU 1353/12-1, OL 241/2-1, and RI 1068/7-1.
+We are thankful for the contributions and discussions with the members of the HPCCF and for the contributions made by the PeCoH project.
+\jk{TODO}
+PeCoH was supported by the German Research Foundation (DFG) under grants LU 1353/12-1, OL 241/2-1, and RI 1068/7-1.
 \end{acks}

### 2019-04-15 paper.tex
Anja's comments.

@@
 \newcommand{\jk}[1]{\todo[inline]{TODO: #1}}
+\newcommand{\ag}[1]{\todo[inline]{IDEA: #1}}
 
@@
 This leads to the prototypical approach for the certification process in \Cref{sec:certification}.
+In \Cref{sec:ecosystem} there the ecosystem is described.
 Related work is presented in \Cref{sec:related}.
@@
   What is the skill trying to achieve?
-  \item \textbf{Learning outcomes (LOs)}: Defines briefly what what practitioners will know and learn.
+  \item \textbf{Learning outcomes (LOs)}: Defines briefly what practitioners will know and learn.
   The objected are statements what prospect learners are able to do, they should
@@
 We believe this is a good granularity as it allows practitioners to cherry-pick the relevant skills and lecturers and examiners to prepare small lectures with well-defined content.
-For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that provide the foundation to many specialized skills each representing a specific hardware or software technology.
-
+\ag{change sentence because provided that provide - \\
+Instead: For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that provide the foundation to many specialized skills each representing a specific hardware or software technology.\\
+write it this way: For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that contribute to the foundation of many specialized skills each representing a specific hardware or software technology.
+}
 The aggregation within the tree is similar to the aggregation found in education as part of “individual teaching events”, “those specified for modules or short courses”, and “those specified for whole degree programmes” \cite{hussey2008learning}.
@@
 Next, we present a generic skill that describes an inner-node in more details.
+\ag{change sentence because delivery and deliver in one sentence - 
 There is no actual delivery as a module or teaching event to deliver the content, it serves the purpose to inform the practitioner about the importance of the skill.
-
+}
 \begin{itemize}
@@
 \end{itemize}
+
+\ag{When I was reading the "learning outcome" of USE4.2B, another category came to mind: 
+How to write job scripts? How to batch use?
+So why not create a case where the learning outcomes overlap?
+Since you did the skill examples with USE4.2 in 4.2, I would not do "Figure 1" with extension of PE4 but USE4.
+Then you can always look there.
+}
 
@@
 \end{itemize}
+
+\ag{I could put my slide set online and show the skill tree for the slide set. An example could be shown, there the content described in a skill tree are also explained in slide sets.
+Everything under USE 4.2.2 B, I have explained it in my slide set under "SLURM Usage on Goethe HLR cluster".
+\\
+What I have found and would like to try it out:  http://xlong88.github.io/draw-binary-tree-latex/
+Create recursive and automatically a Binary Tree with Tikz and Tikz-qtree.
+If we can do it generically then I will be one step ahead with my skill tree for the slide set.
+}
 

### 2019-04-16 paper.tex
Kays comments.

@@
 \newcommand{\ag}[1]{\todo[inline]{IDEA: #1}}
+\newcommand{\kh}[1]{\todo[inline]{KH: #1}}
 
@@
 This leads to the prototypical approach for the certification process in \Cref{sec:certification}.
-In \Cref{sec:ecosystem} there the ecosystem is described.
+In \Cref{sec:ecosystem} there\kh{Vorschlag: ohne there} the ecosystem is described.
 Related work is presented in \Cref{sec:related}.
@@
 
-The forum is organized using a Webpage\footnote{http://hpc-certification.org} and utilizes Slack for communication and monthly meetings.
+The forum is organized using a Webpage\footnote{http://hpc-certification.org} and utilizes Slack\kh{Vorschlag: kurzen Hinweis zu Slack ergänzen "...
+cloud-based set of proprietary team collaboration tools ..." bzw.
+Link auf die Website} for communication and monthly meetings.
 Members are organized in different roles:
@@
 We also established relations with various stackholders involved in HPC education growing the participation in the forum.
-Meeting notes with action items are extracted from Slack and documented using Google Doc.
+Meeting notes with action items are extracted from Slack and documented using Google Doc\kh{Vorschlag: kurze Info zum Tool bzw. Link (wie bei Slack) ergänzen}.
 
 Note that until now contributions of members are voluntarily and follow the schedule as agreed between the contributor and the HPCCF board.
-We manage the prospect contributions in a Trello board; each member can manage its own card.
+We manage the prospect contributions in a Trello board\kh{Vorschlag: kurze Info zum Tool bzw.
+Link (wie bei Slack und Google Doc) ergänzen (Trello kennt ja nicht unbedingt jeder Leser); der Begriff "collaborative" sollte irgendwo untergebracht werden}; each member can manage its own card.
 
-\paragraph{Technical}
+\paragraph{Technical}\kh{"Management" (oberhalb) finde ich auf der Ebene alleinstehend gut, "Technical" etwas zu kurz, Vorschlag: "Technical Tasks" (o.ä.)}
 According to our goals, we address 1) the definition of competences; 2) the creation of certificates; 3) the examination of practitioners; and 4) an ecosystem of tools supporting them.
@@
 A skill is defined as a set of competences (learning outcomes) and some metadata.
-This model can be compared to the classification of school knowledge, for example, the skill with the short name “addition” could describe the math skill of being able to add numbers successfully.
+This model can be compared to the classification of school knowledge, for example, the skill with the short name “addition” could describe the math skill of being able to add numbers successfully.\kh{ich halte ein prägnantes und gutes Beispiel hier für wichtig.
+Ohne den Übergang zum Expert Level gefällt mir die "Addition" auch gut, aber der Übergang zu "Expert" mit dem Addieren mehrerer Zahlen ist zwar auf abstrakter Ebene ok, aber doch etwas weit entfernt von der Praxis; so spontan fällt mir als analoges alternatives Beispiel aus dem Bereich der Geometrie das Zeichnen einer Geraden mit dem Lineal ("Basic Level") oder die Konstruktion eines Sechsecks mit Zirkel und Lineal ("Expert Level") ein}.
 Within a single skill, there can also be multiple levels (basic, intermediate, expert level) building upon each other that distinguish the expertise further.
@@
 While that Hussey et al.
-conclude that LOs on the coarse grained level are not useful for high-level education, we use a similar concept, but relax the granularity/abstraction level of the learning outcome.
+conclude that LOs on the coarse grained level are not useful for high-level education, we use a similar concept, but relax the granularity/abstraction level of the learning outcome.\kh{den Satz habe ich nicht genau verstanden; als Leser würde ich mir die Kurzbegründung wünschen, die Hussey et al.
+für ihre Feststellung anführen}
 
@@
 
-The following skill describes a leaf-level skill for the usage of SLURM in the basic level.
+The following skill describes a leaf-level skill for the usage of SLURM in\kh{at} the basic level.
 While there is no formal dependency to the introduction (skill USE4.2.2-B), it is expected that practitioners have obtained the other skill before learning this one.
@@
   \item \textbf{Name}: SLURM Workload manager
-  \item \textbf{Background}: SLURM is a widely used open-source workload manager providing various advanced features.
+  \item \textbf{Background}: SLURM is a widely used open-source workload manager providing various advanced features\kh{Vorschlag: einige der Highlights anführen: "... , like ..."}.
   \item \textbf{Aims}:
@@
   \item run interactive jobs with salloc, a batch job with sbatch
-  \item explain the architecture of SLURM, i.e., the role of slurmd, srun and the injection of environment variables
+  \item explain the architecture of SLURM, i.e., the role of slurmd\kh{slurmd haben wir beim "Basic Level" bisher nicht vorgesehen}, srun and the injection of environment variables
   \item explain the function of the tools: sacct, sbatch, salloc, srun, scancel, squeue, sinfo
@@
   \item comprehend that environment variables are set when running a job
-  \item comprehend and describe the expected behavior of a simple job scripts
+  \item comprehend and describe the expected behavior of a simple job scripts\kh{typo?}
   \item comprehend how variables are prioritized when using command line and a script
@@
 Secondly, a text file is given to the user that provides the same information.
-It is PGP signed using the private key of the HPC Certification Forum to allow verification with the published public key.
+It is PGP signed using the private key of the HPC Certification Forum to allow verification with the published\kh{"published" wäre redundant} public key.
 It also contains a verification URL that can be given to a third-party allowing verification of the information.
@@
 \end{figure}
+\kh{Vorschlag: "The basic certificate" ist ja sehr generisch und verlangt vom Leser (vermeidbares) Abstraktionsvermögen; ein prägnantes und praxsinahes Beispiel erscheint mir hier geeigneter}
 
@@
 The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material
-registers a link to the material or course and their email address on our webpage using an online form.
+registers a link to the material or course and their\kh{Plural hier beabsichtigt (Bezug?)} email address on our webpage using an online form.
 That way, the HPCCF is informed about the usage of the seal.
@@
 
-\subsection{Navigation}
+\subsection{Navigation}\kh{Vorschlag Unterkapitel in "Results" umbenennen oder an anderer Stelle aus "Erwartungsgründen" ein "Results"-Kapitel ergänzen (am besten natürlich auf der Hauptgliederungsebene, aber das wird vermutlich schwierig werden)}
 %\paragraph{Navigation}
@@
 Tailor skill-tree specifically to users
-Correlate lack of skills with efficient us
+Correlate lack of skills with efficient us\kh{diese Subsection ist vermutlich noch in Arbeit; Groß-/ Kleinschreibung?}
 

### 2019-04-16 paper.tex
added some of Lev's suggestions - 2,3 & 4

@@
   The HPC community has always considered the training of new and existing HPC practitioners to be of high importance to its growth.
-  This diversification of HPC practitioners challenges the traditional training approaches, which are not able to satisfy the specific needs of users, often coming from non-traditionally HPC disciplines, and only interested in learning a particular set of competences.
+  This diversification of HPC practitioners challenges the traditional training approaches, which are not able to satisfy the specific needs of users, often coming from non-traditionally HPC disciplines, and only interested in learning a particular set of competencies.
   Challenges for HPC centres are to identify and overcome the gaps in users’ knowledge, while users struggle to identify relevant skills.
 
-  With the HPC Certification Forum we aim to clearly categorize, define, and examine competences which brings benefit to all stakeholders involved in training.
+  With the HPC Certification Forum we aim to clearly categorize, define, and examine competencies which brings benefit to all stakeholders involved in training.
   In this article, we report the status and progress this independent body has made during the first year of its existence: processes and prototypes have been drafted that will  mature to a holistic ecosystem beneficial for all stackholders in HPC education.
@@
 This skill set depends on the role and domain of the practitioner but also on the available infrastructure of the center providing the computing resources.
-For example, a scientist needing to run an application on a specific machine may need basic skills in Linux, MPI, environment modules, and knowledge about the batch scheduler, e.g., SLURM.
-Understanding SLURM is a good example of a very fine-grained skill, indeed we can identify “resource management” as a generic skill that illustrates concepts across the rich variety of available resource managers.
+For example, a scientist needing to run an application on a specific machine may need basic skills in Linux, MPI, environment modules, and knowledge about the batch scheduler, e.g., Slurm.
+Understanding Slurm is a good example of a very fine-grained skill, indeed we can identify “resource management” as a generic skill that illustrates concepts across the rich variety of available resource managers.
 Institutions which operate HPC systems typically offer regularly teaching events about general aspects of their supercomputer's hard- and software architecture and about the software environment around parallel programming and optimization.
@@
 Then, an overview of the status is given in \Cref{sec:status}.
-Next, the organization of competences is discussed in \Cref{sec:skills}.
+Next, the organization of competencies is discussed in \Cref{sec:skills}.
 This leads to the prototypical approach for the certification process in \Cref{sec:certification}.
@@
 The HPC Certification Forum (HPCCF) has the role of a (virtual) central authority to curate and maintain a certification program.
-The program consists of the definition of competences, the creation of certificates, and the examination of practitioners to attest that they possess certain competences.
-Moreover, the forum supports tools and an ecosystem around the competences.
+The program consists of the definition of competencies, the creation of certificates, and the examination of practitioners to attest that they possess certain competencies.
+Moreover, the forum supports tools and an ecosystem around the competencies.
 
-The HPCCF aims to support existing activities and complements them by providing a unified and clear way of mapping out the relevant HPC competences for practitioners.
+The HPCCF aims to support existing activities and complements them by providing a unified and clear way of mapping out the relevant HPC competencies for practitioners.
 Thus, the HPCCF does not regulate the content of training material; we purposely separate the definition of skills and certificates with their examinations from content delivery.
@@
 \paragraph{Technical}\kh{"Management" (oberhalb) finde ich auf der Ebene alleinstehend gut, "Technical" etwas zu kurz, Vorschlag: "Technical Tasks" (o.ä.)}
-According to our goals, we address 1) the definition of competences; 2) the creation of certificates; 3) the examination of practitioners; and 4) an ecosystem of tools supporting them.
+According to our goals, we address 1) the definition of competencies; 2) the creation of certificates; 3) the examination of practitioners; and 4) an ecosystem of tools supporting them.
 
 For all these sub-goals we made substantial progress.
-While the definition and organization of competences was the main focus, we prototyped various tools and processes that embed the competences into the wider education ecosystem.
+While the definition and organization of competencies was the main focus, we prototyped various tools and processes that embed the competencies into the wider education ecosystem.
 
 Firstly, we finalized the templates for the description of a competence considering pedagogic literature from higher education.
-We are still working on mapping out all relevant competences, but included also new topics that will be covered in the first version of the certification program.
+We are still working on mapping out all relevant competencies, but included also new topics that will be covered in the first version of the certification program.
 
-The definition of the competences covered by the program is version controlled with Git.
-The competences are available in XML and Markdown format.
-A Wiki allows to edit the competences and simplifies access for non-technical users.
+The definition of the competencies covered by the program is version controlled with Git.
+The competencies are available in XML and Markdown format.
+A Wiki allows to edit the competencies and simplifies access for non-technical users.
 A navigable JavaScript representation of the skill tree is available that can be customized for the HPCCF but also for end-users.
@@
 
-A skill is defined as a set of competences (learning outcomes) and some metadata.
+A skill is defined as a set of competencies (learning outcomes) and some metadata.
 This model can be compared to the classification of school knowledge, for example, the skill with the short name “addition” could describe the math skill of being able to add numbers successfully.\kh{ich halte ein prägnantes und gutes Beispiel hier für wichtig.
@@
 	\includegraphics[width=15.0cm]{skill-tree}
-	\caption{Skill tree top level competences with an expansion of PE4}
+	\caption{Skill tree top level competencies with an expansion of PE4}
 	\label{fig:skill-tree}
@@
 
-The following skill describes a leaf-level skill for the usage of SLURM in\kh{at} the basic level.
+The following skill describes a leaf-level skill for the usage of Slurm in\kh{at} the basic level.
 While there is no formal dependency to the introduction (skill USE4.2.2-B), it is expected that practitioners have obtained the other skill before learning this one.
@@
   \item \textbf{ID}: USE4.2.2-B
-  \item \textbf{Name}: SLURM Workload manager
-  \item \textbf{Background}: SLURM is a widely used open-source workload manager providing various advanced features\kh{Vorschlag: einige der Highlights anführen: "... , like ..."}.
+  \item \textbf{Name}: Slurm Workload manager
+  \item \textbf{Background}: Slurm is a widely used open-source workload manager providing various advanced features\kh{Vorschlag: einige der Highlights anführen: "... , like ..."}.
   \item \textbf{Aims}:
   \begin{itemize}
-    \item To enable practitioners to use relevant tools to run and monitor parallel applications using SLURM.
-    \item To enable practitioners to comprehend and describe the basic architecture of SLURM and the suite of tools.
+    \item To enable practitioners to use relevant tools to run and monitor parallel applications using Slurm.
+    \item To enable practitioners to comprehend and describe the basic architecture of Slurm and the suite of tools.
   \end{itemize}
@@
   \item run interactive jobs with salloc, a batch job with sbatch
-  \item explain the architecture of SLURM, i.e., the role of slurmd\kh{slurmd haben wir beim "Basic Level" bisher nicht vorgesehen}, srun and the injection of environment variables
+  \item explain the architecture of Slurm, i.e., the role of Slurmd\kh{Slurmd haben wir beim "Basic Level" bisher nicht vorgesehen}, srun and the injection of environment variables
   \item explain the function of the tools: sacct, sbatch, salloc, srun, scancel, squeue, sinfo
@@
 \ag{I could put my slide set online and show the skill tree for the slide set. An example could be shown, there the content described in a skill tree are also explained in slide sets.
-Everything under USE 4.2.2 B, I have explained it in my slide set under "SLURM Usage on Goethe HLR cluster".
+Everything under USE 4.2.2 B, I have explained it in my slide set under "Slurm Usage on Goethe HLR cluster".
 \\
@@
 
-As you can see from the definition of the skill, these learning outcomes are focusing on the core needs to actually use SLURM effectively.
+As you can see from the definition of the skill, these learning outcomes are focusing on the core needs to actually use Slurm effectively.
 An intermediate skill could, e.g., add reservations.
@@
 
-The summative assessment itself is conducting using multiple choice questions.
+The summative assessment itself is conducted using multiple choice questions.
 Therefore, for each skill, we will be developing a pool of questions but also allow contribution of questions.
@@
 Validate knowledge via tests
-Browse of relevant competences
+Browse of relevant competencies
 Identify recommended and required skills
@@
 Moreover, it would allow centres to bundle together skills that are most beneficial for specific user roles and scientific domains.
-From the perspective of content providers, existing training material can be mapped to competences allowing users to quickly identify and learn the skills they require.
+From the perspective of content providers, existing training material can be mapped to competencies allowing users to quickly identify and learn the skills they require.
 Finally, the certificates recognized by the whole HPC community simplify inter-comparison of independently offered courses and provide additional incentive for participation.

### 2019-04-16 paper.tex
new abstract

@@
 \begin{abstract}
-  The HPC community has always considered the training of new and existing HPC practitioners to be of high importance to its growth.
-  This diversification of HPC practitioners challenges the traditional training approaches, which are not able to satisfy the specific needs of users, often coming from non-traditionally HPC disciplines, and only interested in learning a particular set of competencies.
-  Challenges for HPC centres are to identify and overcome the gaps in users’ knowledge, while users struggle to identify relevant skills.
 
-  With the HPC Certification Forum we aim to clearly categorize, define, and examine competencies which brings benefit to all stakeholders involved in training.
-  In this article, we report the status and progress this independent body has made during the first year of its existence: processes and prototypes have been drafted that will  mature to a holistic ecosystem beneficial for all stackholders in HPC education.
+The ever-changing nature of HPC has always compelled the HPC community to focus a lot of effort into training of new and existing practitioners. Historically, these efforts were tailored
+ around a typical group of users possessing, due to their background, a certain set of programming skills. However, as HPC has become more diverse in terms of hardware, software and 
+ the user background, the traditional training approaches became insufficient in addressing training needs of our community. This increasingly complicated HPC landscape makes 
+ developement and delivery of new training materials challenging. How should we develop training for users, often coming from non-traditionally HPC disciplines, and only interested in 
+ learning a particular set of skills? How can we satisfy their training needs if we don't really understand what these are? It's clear that HPC centres struggle to identify and overcome the 
+ gaps in users' knowledge, while users struggle to identify skills required to perform their tasks.
+
+With the HPC Certification Forum we aim to clearly categorise, define, and examine competencies expected from proficient HPC practitioners. 
+In this article, we report the status and progress this independent body has made during the first year of its existence. The drafted processes and prototypes are expected to mature into a 
+holistic ecosystem beneficial for all stakeholders in HPC education.
 \end{abstract}

### 2019-04-16 paper.tex
edited Introduction

@@
 For example, a scientist needing to run an application on a specific machine may need basic skills in Linux, MPI, environment modules, and knowledge about the batch scheduler, e.g., Slurm.
-Understanding Slurm is a good example of a very fine-grained skill, indeed we can identify “resource management” as a generic skill that illustrates concepts across the rich variety of available resource managers.
-Institutions which operate HPC systems typically offer regularly teaching events about general aspects of their supercomputer's hard- and software architecture and about the software environment around parallel programming and optimization.
-The learning material provided by an HPC center, however, is geared to the special demands of the institutions they support and its specific HPC environment.
-This content typically covers a small part of basic HPC skills which are necessary to use other HPC systems.
-Moreover, they do not attest the users to have a certain competence.
-Certificates are widely used in industry to attest certain knowledge but, so far, there is no similar approach for HPC training.
+Now rather than providing that scientists with a list of instructions to be followed in a copy and paste fashion or a never-ending list of things they should know, we want them to understand each of the required steps without having to learner everything about it, but at the same time understand how it fits into the bigger picture of using an HPC system.
+For instance, understanding Slurm is a good example of a very fine-grained skill that fits under a more generic skill defined as "resource management", illustrating concepts across the rich variety of available resource managers.
 
-This article describes the current status of the certification program offered by the HPC Certification Forum.
-Our previous work provided a brief overview of the evolution from the project that sparked  the HPC Certification Forum \cite{TAHCPKHHSS19} while this article provides details highlighting mechanisms and design decisions.
+Most institutions operating HPC systems offer regular training events focusing on general aspects of their supercomputer's hardware architecture, software stack, application development environment  and various tuning and debugging tools.
+It is understandable why the materials they are geared towards the special demands of the institutions they support and its specific HPC environment. 
+The problem is that teaching content typically covers only a small part of basic HPC skills necessary to use other HPC systems. 
+This approach of teaching only specific implementations, tools or workflows, instead of concepts behind them makes a move to a different system or tool unnecessary complicated. 
+Narrowing the scope of training events make sense from the HPC provider perspective, but is not very conducive to development of more comprehensive learning environment that provides assessment and certifies the newly acquired skills.
+So although, certificates are used widely in IT industry to verify certain knowledge, until now there was no similar approach for HPC training.
+It is, however, clear that a certification scheme could address some of the challenges stemming from the constantly growing training needs of our community,
+
+This article describes the current status of the certification program initiated by the HPC Certification Forum.
+Our previous work provided a brief overview of the evolution from the project that sparked the HPC Certification Forum \cite{TAHCPKHHSS19} while this article provides details on adopted mechanisms and design decisions.
 
 The article is structured as follows:
-First, we introduce the HPC Certification Forum and the program in \Cref{sec:forum}.
-Then, an overview of the status is given in \Cref{sec:status}.
-Next, the organization of competencies is discussed in \Cref{sec:skills}.
-This leads to the prototypical approach for the certification process in \Cref{sec:certification}.
-In \Cref{sec:ecosystem} there\kh{Vorschlag: ohne there} the ecosystem is described.
+First, in \Cref{sec:forum} we introduce the HPC Certification Forum and the certification program. 
+Then, an overview of the status is given in \Cref{sec:status}, followed by the organisation of competencies discussed in \Cref{sec:skills}.
+This leads to the proposal for the certification process in \Cref{sec:certification}.
+In \Cref{sec:ecosystem} the whole learning ecosystem is described.
 Related work is presented in \Cref{sec:related}.

### 2019-04-17 paper.tex
edited The HPC Certification Forum section

@@
 
-The HPC Certification Forum (HPCCF) has the role of a (virtual) central authority to curate and maintain a certification program.
-The program consists of the definition of competencies, the creation of certificates, and the examination of practitioners to attest that they possess certain competencies.
-Moreover, the forum supports tools and an ecosystem around the competencies.
+The HPC Certification Forum (HPCCF) has the role of a (virtual) central authority to curate and maintain the proposed certification program.
+The program consists of three parts: the tree of defined competencies, the examination of practitioners to prove they posses those skills, and finally the certification demonstrating their knowledge.
+Although, the forum is not involved in development of any training materials or tools, it supports the ecosystem around the competencies.
 
-The HPCCF aims to support existing activities and complements them by providing a unified and clear way of mapping out the relevant HPC competencies for practitioners.
-Thus, the HPCCF does not regulate the content of training material; we purposely separate the definition of skills and certificates with their examinations from content delivery.
-Similarly, the program does not prescribe a curriculum or any fixed order by which skills need to be obtained.
+The HPCCF aims to support existing activities and complements them by providing a unified and clear way of mapping out the relevant HPC competencies.
+Thus, the HPCCF does not regulate the content of training material; we purposely separate the definition of skills, the examination and the certification from content delivery.
+Similarly, the program does not prescribe a curriculum or any fixed order by which skills need to be obtained. It eases the navigation between different competencies without being overly restrictive.
 
-The forum is organized using a Webpage\footnote{http://hpc-certification.org} and utilizes Slack\kh{Vorschlag: kurzen Hinweis zu Slack ergänzen "...
-cloud-based set of proprietary team collaboration tools ..." bzw.
-Link auf die Website} for communication and monthly meetings.
-Members are organized in different roles:
-Anyone can become an associate member in the HPCCF free of charge -- e.g., observing the status, being listed on the webpage.
-Full members must actively contribute to the program to some extent and have voting rights for the roles of the steering board.
-The steering board directs the overall activities and is organized in different responsibilities, i.e., into topic-specific chairs.
+The forum is organised around a Webpage\footnote{http://hpc-certification.org},  a GitHub repository\footnote{https://github.com/HPC-certification-forum},  and a could-based team collaboration tool (Slack) for communication and monthly meetings.
+The membership is divined into three categories: associate, full and steering board.   
+Anyone can become an associate member free of charge, allowing a passive involvement -- e.g., observing the status, being listed on the webpage.
+Full members must actively contribute to the program and have voting rights for the roles of the steering board.
+The steering board directs the overall activities and is organised in different responsibilities, i.e., into topic-specific chairs. At the moment the steering board has 9 members.
 
@@
 At beginning we used video conferencing tools, but found that the chat provides a more inclusive discussion and the asynchronous nature is more productive.
-We also established relations with various stackholders involved in HPC education growing the participation in the forum.
+We also established relations with various stakeholders involved in HPC education growing the participation in the forum.
 Meeting notes with action items are extracted from Slack and documented using Google Doc\kh{Vorschlag: kurze Info zum Tool bzw. Link (wie bei Slack) ergänzen}.

### 2019-04-17 paper.tex
Trivial changes.
Nai

@@
  the user background, the traditional training approaches became insufficient in addressing training needs of our community. This increasingly complicated HPC landscape makes
- developement and delivery of new training materials challenging. How should we develop training for users, often coming from non-traditionally HPC disciplines, and only interested in 
+ development and delivery of new training materials challenging. How should we develop training for users, often coming from non-traditionally HPC disciplines, and only interested in
  learning a particular set of skills? How can we satisfy their training needs if we don't really understand what these are? It's clear that HPC centres struggle to identify and overcome the
@@
 So although, certificates are used widely in IT industry to verify certain knowledge, until now there was no similar approach for HPC training.
-It is, however, clear that a certification scheme could address some of the challenges stemming from the constantly growing training needs of our community,
+It is, however, clear that a mapping of competences and certification scheme could address some of the challenges stemming from the constantly growing training needs of our community,
 

### 2019-04-17 paper.tex
Changed example to HPC driving license.

@@
 A PDF with the key information needed for a meaningful certificate (for a draft, see \Cref{fig:awardedCertificate}).
-The name and identifier for the certificate is found in the center and below (here 4711 and “the basic certificate”).
+The name and identifier for the certificate is found in the center and below (here 1 and “HPC Driving License”).
+Similar to a driving license, this particular certificate could provide the minimum set of knowledge to understand and use a generic supercomputer.
 
 Secondly, a text file is given to the user that provides the same information.
-It is PGP signed using the private key of the HPC Certification Forum to allow verification with the published\kh{"published" wäre redundant} public key.
+It is PGP signed using the private key of the HPC Certification Forum to allow verification with the  public key.
 It also contains a verification URL that can be given to a third-party allowing verification of the information.
@@
 successfully obtained the certificate
-"The basic certificate" (id: 4711) at 02/2019.
+"HPC driving license" (id: 1) at 02/2019.
 Verification URL: https://hpc-certification.org/[...]
@@
 \end{figure}
-\kh{Vorschlag: "The basic certificate" ist ja sehr generisch und verlangt vom Leser (vermeidbares) Abstraktionsvermögen; ein prägnantes und praxsinahes Beispiel erscheint mir hier geeigneter}
 

### 2019-04-17 paper.tex
Resolved some low-hanging fruits.

@@
 
-\newcommand{\jk}[1]{\todo[inline]{TODO: #1}}
-\newcommand{\ag}[1]{\todo[inline]{IDEA: #1}}
+\newcommand{\jk}[1]{\todo[inline]{JK: #1}}
+\newcommand{\ag}[1]{\todo[inline]{Anja: #1}}
 \newcommand{\kh}[1]{\todo[inline]{KH: #1}}
@@
 
-\paragraph{Technical}\kh{"Management" (oberhalb) finde ich auf der Ebene alleinstehend gut, "Technical" etwas zu kurz, Vorschlag: "Technical Tasks" (o.ä.)}
+\paragraph{Technical tasks}
 According to our goals, we address 1) the definition of competencies; 2) the creation of certificates; 3) the examination of practitioners; and 4) an ecosystem of tools supporting them.
@@
 
-Next, we present a generic skill that describes an inner-node in more details.
-\ag{change sentence because delivery and deliver in one sentence -
-There is no actual delivery as a module or teaching event to deliver the content, it serves the purpose to inform the practitioner about the importance of the skill.
-}
+Next, we present a generic competence that describes an inner-node of the skill tree in more details.
+
 \begin{itemize}
@@
 
-The following skill describes a leaf-level skill for the usage of Slurm in\kh{at} the basic level.
+The following skill describes a leaf-level skill for the usage of Slurm at the basic level.
 While there is no formal dependency to the introduction (skill USE4.2.2-B), it is expected that practitioners have obtained the other skill before learning this one.
@@
   \item \textbf{Name}: Slurm Workload manager
-  \item \textbf{Background}: Slurm is a widely used open-source workload manager providing various advanced features\kh{Vorschlag: einige der Highlights anführen: "... , like ..."}.
+  \item \textbf{Background}: Slurm is a widely used open-source workload manager providing various advanced features.
+% \kh{Vorschlag: einige der Highlights anführen: "...
+, like ..."}.
+Good idea, but later!
   \item \textbf{Aims}:
@@
   \item run interactive jobs with salloc, a batch job with sbatch
-  \item explain the architecture of Slurm, i.e., the role of Slurmd\kh{Slurmd haben wir beim "Basic Level" bisher nicht vorgesehen}, srun and the injection of environment variables
+  \item explain the architecture of Slurm, i.e., the role of Slurmd, srun and the injection of environment variables
   \item explain the function of the tools: sacct, sbatch, salloc, srun, scancel, squeue, sinfo
@@
   \item comprehend that environment variables are set when running a job
-  \item comprehend and describe the expected behavior of a simple job scripts\kh{typo?}
+  \item comprehend and describe the expected behavior of a simple job script
   \item comprehend how variables are prioritized when using command line and a script
@@
 The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material
-registers a link to the material or course and their\kh{Plural hier beabsichtigt (Bezug?)} email address on our webpage using an online form.
+registers a link to the material or course on our webpage using an online form. %\footnote{Details of the link will show the email address.}
 That way, the HPCCF is informed about the usage of the seal.

### 2019-04-17 paper.tex
edited the Overview of the actities section

--- 2019-04-17 paper.tex
@@
  the user background, the traditional training approaches became insufficient in addressing training needs of our community. This increasingly complicated HPC landscape makes 
- development and delivery of new training materials challenging. How should we develop training for users, often coming from non-traditionally HPC disciplines, and only interested in
+ developement and delivery of new training materials challenging. How should we develop training for users, often coming from non-traditionally HPC disciplines, and only interested in 
  learning a particular set of skills? How can we satisfy their training needs if we don't really understand what these are? It's clear that HPC centres struggle to identify and overcome the 
@@
 So although, certificates are used widely in IT industry to verify certain knowledge, until now there was no similar approach for HPC training.
-It is, however, clear that a mapping of competences and certification scheme could address some of the challenges stemming from the constantly growing training needs of our community,
+It is, however, clear that a certification scheme could address some of the challenges stemming from the constantly growing training needs of our community,
 
@@
 
-During the first year of the existence of the HPCCF, the discussion within the forum and with partners has lead to the establishment of various processes and prototypes for technical tools that are described in the following briefly.
-Further details of the overview are provided in subsequent sections.
+The first year of the HPCCF forum was rich in discussions, both internally and with external partners, resulting in a number of processes and prototype tools being put in place.
+These are described briefly below, and in more details in the subsequent sections.
 
 \paragraph{Management}
-At ISC-HPC 2018, the first steering board had been elected.
+The first steering board has been elected at ISC-HPC 2018.
 We established communication channels via webpage, email and Slack for regular discussion.
 Slack is also used to conduct our monthly open meetings between members and the steering board.
-At beginning we used video conferencing tools, but found that the chat provides a more inclusive discussion and the asynchronous nature is more productive.
-We also established relations with various stakeholders involved in HPC education growing the participation in the forum.
-Meeting notes with action items are extracted from Slack and documented using Google Doc\kh{Vorschlag: kurze Info zum Tool bzw. Link (wie bei Slack) ergänzen}.
+At beginning video conferencing tools have been used, but the geographical diversity of the attendees influenced the decision to move towards chat-based tools. 
+The asynchronous nature and automatic message retention proved to be more productive, and provided a more open and inclusive platform for discussion.    
+Meeting notes with action items are extracted from Slack and documented using Google Doc (an online word processor allowing a real-time and multiple-user collaboration).
 
-Note that until now contributions of members are voluntarily and follow the schedule as agreed between the contributor and the HPCCF board.
-We manage the prospect contributions in a Trello board\kh{Vorschlag: kurze Info zum Tool bzw.
-Link (wie bei Slack und Google Doc) ergänzen (Trello kennt ja nicht unbedingt jeder Leser); der Begriff "collaborative" sollte irgendwo untergebracht werden}; each member can manage its own card.
+The ongoing conversation with various stakeholders involved in HPC education and training, keeps producing more engagement in the forum's activities.   
+The member's contributions are voluntarily and follow the schedule agreed between the contributor and the HPCCF board.
+The prospective contributions are managed in Trello (a web-based list-making collaborative application), in which each member can manage their own card.
 
-\paragraph{Technical}\kh{"Management" (oberhalb) finde ich auf der Ebene alleinstehend gut, "Technical" etwas zu kurz, Vorschlag: "Technical Tasks" (o.ä.)}
-According to our goals, we address 1) the definition of competencies; 2) the creation of certificates; 3) the examination of practitioners; and 4) an ecosystem of tools supporting them.
+\paragraph{Technical Tasks}
+The tasks we set out to accomplish are:  1) the definition of competencies; 2) the examination of practitioners;  3) the creation of certificates; and 4) the reinforcement of an ecosystem of tools supporting them.
 
 For all these sub-goals we made substantial progress.
-While the definition and organization of competencies was the main focus, we prototyped various tools and processes that embed the competencies into the wider education ecosystem.
+While the definition and organisation of competencies was the main focus, we prototyped various tools and processes that embed the competencies into the wider education ecosystem.
 
-Firstly, we finalized the templates for the description of a competence considering pedagogic literature from higher education.
-We are still working on mapping out all relevant competencies, but included also new topics that will be covered in the first version of the certification program.
+Firstly, considering the pedagogic literature from higher education we finalised the templates for the skills description. 
+The effort to map out all of the relevant competencies is still on-going, but the feedback received during a number of events organised by the HPCCF and other members of the HPC education community resulted in the addition of new topics to the first version of the certification program.
 
-The definition of the competencies covered by the program is version controlled with Git.
-The competencies are available in XML and Markdown format.
-A Wiki allows to edit the competencies and simplifies access for non-technical users.
-A navigable JavaScript representation of the skill tree is available that can be customized for the HPCCF but also for end-users.
+The definitions of the competencies are version controlled with Git, and are publicly available in XML and Markdown format.
+A Wiki\footnote{https://www.hpc-certification.org/wiki/} is being used to edit the skills' descriptions, and a navigable and widely customisable JavaScript\footnote{https://www.hpc-certification.org/skills/map/} makes the skill tree easily accessible to the forum members and the end-users alike.
 
-Prototypical processes and tools have been developed and deployed for curation of the examination questions and for conducting an online multiple-choice examination.
+Premilinary processes and tools have been developed and deployed for curation of the examination questions and for conducting an online multiple-choice examination.
 

### 2019-04-17 paper.tex

@@
 
-\paragraph{Technical Tasks}
+\paragraph{Technical tasks}
 The tasks we set out to accomplish are:  1) the definition of competencies; 2) the examination of practitioners;  3) the creation of certificates; and 4) the reinforcement of an ecosystem of tools supporting them.
@@
 
-Next, we present a generic skill that describes an inner-node in more details.
-\ag{change sentence because delivery and deliver in one sentence - 
-There is no actual delivery as a module or teaching event to deliver the content, it serves the purpose to inform the practitioner about the importance of the skill.
-}
+Next, we present a generic competence that describes an inner-node of the skill tree in more details.
+
 \begin{itemize}

### 2019-04-17 paper.tex
edited the Skills section

@@
 
-\section{Overview of the Activities}
+\section{Overview of the HPCCF activities}
 \label{sec:status}
@@
 
-Premilinary processes and tools have been developed and deployed for curation of the examination questions and for conducting an online multiple-choice examination.
+Preliminary processes and tools have been developed and deployed for curation of the examination questions and for conducting an online multiple-choice examination.
 
@@
 
-A skill is defined as a set of competencies (learning outcomes) and some metadata.
-This model can be compared to the classification of school knowledge, for example, the skill with the short name “addition” could describe the math skill of being able to add numbers successfully.\kh{ich halte ein prägnantes und gutes Beispiel hier für wichtig.
-Ohne den Übergang zum Expert Level gefällt mir die "Addition" auch gut, aber der Übergang zu "Expert" mit dem Addieren mehrerer Zahlen ist zwar auf abstrakter Ebene ok, aber doch etwas weit entfernt von der Praxis; so spontan fällt mir als analoges alternatives Beispiel aus dem Bereich der Geometrie das Zeichnen einer Geraden mit dem Lineal ("Basic Level") oder die Konstruktion eines Sechsecks mit Zirkel und Lineal ("Expert Level") ein}.
-Within a single skill, there can also be multiple levels (basic, intermediate, expert level) building upon each other that distinguish the expertise further.
-We expect that practitioners acquire the lower levels before progressing to more complex levels.
-In our addition example, \textit{basic level}, for example, may mean to be able to add two positive numbers while the \textit{expert level} of that skill could indicate to be able to add multiple numbers.
+A skill is defined as a set of learning outcomes and relevant metadata. 
+Within a single skill, there can also be multiple levels (basic, intermediate and expert level) building upon each other and further distinguishing the expertise. 
+We expect the practitioners to acquire the lower levels before progressing to more complex levels.
 
-The basic level should cover the most relevant aspect of the skill, i.e., needed by anyone that uses the skill, the intermediate level (used for common exceptional cases) and expert levels (used in special circumstances)  are needed only for a subset of users.
-Typically, an institution has only few experts (if one at all).
+This model can be compared to the classification of school knowledge, for example, a skill with the name “basic arithmetic operations” would include the math skills of addition (being able to add numbers), subtraction (being able to subtract numbers), multiplication (being able to multiply numbers) and division (being able to divide numbers).
+Operating on two numbers would be a basic level of the skill, whereas mentally operating on hundreds of numbers would be an expert level.
+Another example could be a skill called "technical drawing", in which being able to draw simple geometric figures would be counted as a basic level, and an ability to draw a complicated mechanical objects would be an expert level.
 
-The skills are organized in a tree that serves the purpose to organize and structure the skills from a coarse-grained to a fine-grained representation allowing users to browse the skill based on the semantics.
-The root level of our current skill tree is shown in \Cref{fig:skill-tree}; we aim to finalize the tree this year.
-The basic idea is that the skills from the root level enable navigation by providing an indication about their scope, e.g., are they core knowledge, dealing with the usage of HPC environments, or about programming.
+The basic level should cover the most relevant aspect of the skill (needed by anyone that uses the skill), whereas the intermediate (used for common exceptional cases) and expert levels (used in special circumstances)  are needed only for a subset of users.
+Typically, an institution has only few experts, if any at all.
+
+The skills are organised in a tree structure from a coarse-grained to a fine-grained representation, allowing users to browse the skill based on the semantics.
+The root level of our current skill tree is shown in \Cref{fig:skill-tree}. The goal is to finalise the tree this year.
+The basic idea is that the skills from the root level simplify the navigation by providing an indication about their scope, e.g., core knowledge, usage of HPC environments, or about programming.
 This should allow the user to rapidly drill into the skill representation.
-The closer a skill is to the root, the more abstract it is defined, while leaf nodes cover the knowledge for the specific skill.
+The closer a skill is to the root, the more abstractly it is defined, while leaf nodes cover the knowledge for a specific skill.
 
-As the tree serves the purpose to organize the skills, there can also be references from one branch to a skill in another.
-This import allows to reuse the definitions of the skills while still allowing users to navigate the tree according to the semantics.
+As the tree serves the purpose of organising the skills, the references from one branch to a skill in another branch are allowed.
+This import feature makes the reuse of the skill definitions possible, at the same time allowing users to navigate the tree according to the semantics.
 
@@
 	\includegraphics[width=15.0cm]{skill-tree}
-	\caption{Skill tree top level competencies with an expansion of PE4}
+	\caption{Skill tree: top level competencies with the PE4 branch expanded.}
 	\label{fig:skill-tree}
@@
 \begin{itemize}
-  \item \textbf{ID}: ID according the organization in the skill tree. The last character indicates the level of the skill (Basic, Intermediate, or Advanced).
+  \item \textbf{ID}: ID according the organisation in the skill tree. The last character indicates the level of the skill (Basic, Intermediate, or Advanced).
   \item \textbf{Name}: A speaking name for the skill.

### 2019-04-17 paper.tex
edited the Description of a skill section

@@
 
-Each skill on the tree and even the inner nodes are described in more detail as follows:
+Each skill on the tree, including the inner nodes, is described in more detail as follows:
 
 \begin{itemize}
-  \item \textbf{ID}: ID according the organisation in the skill tree. The last character indicates the level of the skill (Basic, Intermediate, or Advanced).
-  \item \textbf{Name}: A speaking name for the skill.
-  \item \textbf{Background}: Provides brief information motivating the need for the skill and how this skill fits into the skill tree; what is the bigger picture.
-  \item \textbf{Aims}\footnote{The definition of aims and outcomes follows literature for higher education \cite{williamson2011good} and \url{https://www.heacademy.ac.uk/system/files/assessment-learning-outcomes.pdf}.}: They serve as broad purposes and are generally a statement of the intentions of the skill.
-  They are not the statements of what a practitioner will learn or do.
-  At a basic level, aims are trying to answer two questions: What is the purpose of this skill?
-  What is the skill trying to achieve?
-  \item \textbf{Learning outcomes (LOs)}: Defines briefly what practitioners will know and learn.
-  The objected are statements what prospect learners are able to do, they should
-  describe or define an action be clearly stated be measurable/quantifiable to some extent by using action words.
+  \item \textbf{ID}: ID according to its position in the skill tree. The last character indicates the level of the skill (Basic, Intermediate, or Advanced).
+  \item \textbf{Name}: A name capturing the essence of the skill.  
+  \item \textbf{Background}: Provides brief information motivating the need for the skill and how it fits into the bigger picture with other skills. 
+  \item \textbf{Aims}\footnote{The definition of aims and outcomes follows literature for higher education \cite{williamson2011good} and \url{https://www.heacademy.ac.uk/system/files/assessment-learning-outcomes.pdf}.}:
+  Describe the purpose of the skills, but doesn't really include a list of what a practitioner will learn or do.
+Explaining what a skill is trying to achieve is not the same as saying how it should be done.
+  \item \textbf{Learning outcomes (LOs)}: Defines briefly what practitioners will learn.
+  The objectives are statements what prospective learners are able to do.
+They should clearly describe or define an action bringing about a measurable/quantifiable increase in understanding of that skill.
  \end{itemize}
 
-On the leaf level, a skill is fine-grained and orthogonal to other skills -- we scope the level of detail here to be able to be taught in a 1.5 hour lecture up to a 4 hour workshop.
-We believe this is a good granularity as it allows practitioners to cherry-pick the relevant skills and lecturers and examiners to prepare small lectures with well-defined content.
-\ag{change sentence because provided that provide - \\
-Instead: For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that provide the foundation to many specialized skills each representing a specific hardware or software technology.\\
-write it this way: For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that contribute to the foundation of many specialized skills each representing a specific hardware or software technology.
-}
-The aggregation within the tree is similar to the aggregation found in education as part of “individual teaching events”, “those specified for modules or short courses”, and “those specified for whole degree programmes” \cite{hussey2008learning}.
-While that Hussey et al.
-conclude that LOs on the coarse grained level are not useful for high-level education, we use a similar concept, but relax the granularity/abstraction level of the learning outcome.\kh{den Satz habe ich nicht genau verstanden; als Leser würde ich mir die Kurzbegründung wünschen, die Hussey et al.
-für ihre Feststellung anführen}
+On the leaf level, a skill is fine-grained and orthogonal to other skills -- their narrowed scope means they can be taught in sessions ranging from a 1.5 hour lecture up to a 4 hour workshop.
+We believe this granularity allows practitioners to cherry-pick the skills relevant to their circumstances, and lecturers and examiners to prepare small lectures with well-defined content.
+For technology-dependent skills on the leaf level (e.g., a specific file system or workload manager) the introductory skills are often provided, as they contribute to the foundation of many specialised skills representing a specific hardware or software technology.
+
+The aggregation within the tree is similar to that found in the education circles.
+Hussey et al.\cite{hussey2008learning} categorised the aggregation of skills into the following levels: individual teaching events, specified for modules or short courses, and those specified for whole degree programmes.
+Although, Hussey et al.
+conclude that LOs on the coarse grained level are not useful for high-level education, using a similar concept with relaxed level of granularity/abstraction of the learning outcome fits well within the framework of the certification program.
+\kh{den Satz habe ich nicht genau verstanden; als Leser würde ich mir die Kurzbegründung wünschen, die Hussey et al. für ihre Feststellung anführen}
 

### 2019-04-17 paper.tex
edited the Skill Example section

@@
 
-Next, we present a generic competence that describes an inner-node of the skill tree in more details.
+This subsection presents an example of an inner-node skill called "Executing parallel applications", as well as its two leaf skills - "Workload manager introduction" and "Slurm workload manager".
 
@@
   \item \textbf{Background}:
-  Parallel computers are operated differently than a normal PC, all users must share the system.
-Therefore, various operative procedures are in place.
-Users must understand these concepts and procedures to be able to use the available resources of a system to run a parallel application.
-Moreover, individual solutions can often be found in a specific system.
-  \item \textbf{Aim}: To enable practitioners to comprehend the concepts and procedures for running parallel applications in HPC environments.
-  To use the system to run and monitor the execution of parallel applications on the HPC system.
+  Parallel computers are operated differently than a normal PC -- all users share the system.
+To ensure a fair and efficient use of shared resources, various operative procedures are put in place.
+Users must understand these concepts and procedures to be able to run a parallel application on the resources available to them.
+Moreover, different HPC systems adopt different solution to manage their resources.
+  \item \textbf{Aim}: To enable practitioners to comprehend the concepts and procedures for running parallel applications in HPC environments; to run and monitor the execution of parallel applications on HPC systems.
 
@@
     \begin{itemize}
-    \item explain the concepts and procedures for resource allocation and job execution in an HPC environment
-    \item run interactive jobs and batch jobs
-    \item comprehend and describe the expected behavior of job scripts
-    \item change provided job scripts and embed them into shell scripts to run a variety of parallel applications
-    \item analyze the output generated from a job scheduler and describe the cause of typically generated errors
+    \item explain the concepts and procedures related to resource allocation and job execution in an HPC environment;
+    \item run interactive jobs and batch jobs;
+    \item understand and describe the content and expected behaviour of job scripts;
+    \item change provided job scripts and embed them into shell scripts to run a variety of parallel applications;
+    \item analyse the output generated from a job scheduler and understand the cause of typically generated errors.
     \end{itemize}
@@
 
-The next leaf-level skill describes how workload management works in general in HPC regardless of the specific software that implements such concepts.
-It is intended that the aim and outcomes from the parent skill above are covered to some extend and refined into specifics.
+The next leaf-level skill describes how workload management works in general, regardless of the specific software implementing it. 
+The aim and outcomes defined by the parent skill (described above) are expected to be covered (to a certain extend) and refined by this leaf skill.
 
@@
   \item \textbf{Name}: Workload manager introduction
-  \item \textbf{Background}: There is a wide range of different workload managers in use. This skill covers generic and widely used concepts.
-  \item \textbf{Aim}: To enable practitioners to comprehend and describe the basic architecture and concepts of resource allocation for an HPC system.
+  \item \textbf{Background}: There is a wide range of different workload managers in use. This skill on a conceptual level explains how to use them.
+  \item \textbf{Aim}: To enable practitioners to comprehend and describe the basic architecture and concepts of resource allocation on an HPC system.
   \item \textbf{Learning outcomes}:
@@
   \begin{itemize}
-  \item comprehend the exclusive and shared usage model in HPC
-  \item differentiate batch and interactive job submission
-  \item comprehend the generic concepts and architecture of resource manager, scheduler, job and job script
-  \item explain the role of environment variables as a means to communicate
-  \item comprehend accounting principles
-  \item explain the generic steps to run and monitor a single job
+  \item comprehend the exclusive and shared usage model in HPC;
+  \item differentiate between the batch and interactive job submission;
+  \item comprehend the generic concepts and structure of resource manager, scheduler, job and job script;
+  \item explain the role of environment variables as a mean to communicate certain settings of your job;  
+  \item comprehend job budgeting and accounting principles;
+  \item explain the generic steps required run and monitor a single job.
   \end{itemize}
@@
   \item \textbf{Name}: Slurm Workload manager
-  \item \textbf{Background}: Slurm is a widely used open-source workload manager providing various advanced features.
+  \item \textbf{Background}: Slurm is a widely used open-source workload manager, which also provides various advanced features.
 % \kh{Vorschlag: einige der Highlights anführen: "...
@@
     \item To enable practitioners to use relevant tools to run and monitor parallel applications using Slurm.
-    \item To enable practitioners to comprehend and describe the basic architecture of Slurm and the suite of tools.
+    \item To enable practitioners to comprehend and describe the basic structure of Slurm and the related suite of tools.
   \end{itemize}
@@
   \begin{itemize}
-  \item run interactive jobs with salloc, a batch job with sbatch
-  \item explain the architecture of Slurm, i.e., the role of Slurmd, srun and the injection of environment variables
-  \item explain the function of the tools: sacct, sbatch, salloc, srun, scancel, squeue, sinfo
-  \item explain time limits and the benefit of a backfill scheduler
-  \item comprehend that environment variables are set when running a job
-  \item comprehend and describe the expected behavior of a simple job script
-  \item comprehend how variables are prioritized when using command line and a script
-  \item change a provided job template and embed them into shell scripts to run a variety of parallel applications
-  \item analyze the output generated from submitting to the job scheduler and typically generated errors
+  \item run interactive jobs with \textit{salloc}, a batch job with \textit{sbatch};
+  \item explain the architecture of Slurm, i.e., the role of \textit{Slurmd}, \textit{srun} and the injection of environment variables;
+  \item explain the function of the tools: \textit{sacct}, \textit{sbatch}, \textit{salloc}, \textit{srun}, \textit{scancel}, \textit{squeue} and \textit{sinfo};
+  \item explain time limits and the benefit of a backfill scheduler;
+  \item comprehend that environment variables are set when running a job;
+  \item comprehend and describe the expected behaviour of a simple job script;
+  \item comprehend how variables are prioritised when using command line and a script;
+  \item change a provided job template and embed them into shell scripts to run a variety of parallel applications;
+  \item analyse the output generated from submitting to the job scheduler and typically generated errors.
   \end{itemize}
@@
 
-As you can see from the definition of the skill, these learning outcomes are focusing on the core needs to actually use Slurm effectively.
-An intermediate skill could, e.g., add reservations.
+The learning outcomes of this skill, marked with B to indicate its basic level, are focusing on the most fundamental knowledge required to use Slurm effectively.
+An intermediate version of the skill could, for example, cover how to create reservations or special queues.
 

### 2019-04-17 paper.tex
edited the certification section (5 only)

@@
 
-A certificate shall attest a user the expertise in the covered skills.
-Ensuring the integrity of a certificate is an important aspect, i.e., we must check that the learning outcomes of the covered skills are achieved and prevent self-cheating or dishonesty.
+A certificate shall serve as a confirmation that a user obtain the expertise in the relevant skills.
+Special considerations needs to be given to the certification integrity.  
+We must ensure that the learning outcomes of the covered skills are examined to a satisfactory degree, and prevent self-cheating or dishonesty.
+Students can always cheat during an examination -- the susceptibility to cheating depends on many factors, including but not limited to the type of exam, methods used for assessment, motivation for taking it,  consequences of failing or scoring poorly, and the possibility and frequency of resits.
 
-Students can always cheat an examination -- the risk depends on the type of exam and methods used for the assessment.
-As we want to enable a cost-effective assessment (free for the practitioner), we chose an online examination.
-This increases the opportunity for cheating \cite{rowe2004cheating} but we deploy several  strategies that aim to minimize the risk of self-cheating as raising awareness, a question pool, and delay.
-Since knowledge can age, the month and year an examination took place is also indicated.
-As certificates bundle multiple skills together as examination of a single fine-grained leaf-level skill would be too easy for short-term memorization and prone to self-cheating.
-We believe the incentive to deliberately fake the assessment, e.g., by having the exam filled by someone else, and thus, being awarded a certificate is low.
-Therefore, we address this only in a lightweight fashion.
+We want to enable a cost-effective assessment (free for the practitioner), so we chose an online examination.
+This increases the opportunity for cheating \cite{rowe2004cheating} but we plan to deploy a several strategies to minimise the risk of cheating, such as raising the awareness of the examinees, using a pool of questions, and setting time limits for each question.
 
-A process has also been created for prospect contributors of examination questions.
-The questions are the only proprietary component for the HPCCF using restrictive license terms for authors while we give credit to them.
-We considered this necessary to minimize the establishment of solution databases; we omit further details here.
+Since knowledge can age, each certificate needs to indicated when (month and year) the qualifying examination took place.
+Also, because the examination of a single fine-grained leaf-level skill would be too easy for short-term memorisation and more prone to self-cheating, the certificates bundle multiple skills together.
+We believe the incentive to deliberately fake the assessment, e.g., by having the exam filled by someone else, and thus, being awarded a certificate, is low.
+Therefore, we address this issue in a lightweight fashion only.
 
-We discuss the prototypical process that we implemented for conducting examination in the following.
+A process has also been created for prospective contributors of the examination questions.
+The questions are the only proprietary component for the HPCCF -- using restrictive license terms for authors while giving them credit. 
+This is considered necessary to minimise the overhead of managing the database containing solutions to the examination questions.
+
+In the next section, we discuss the process proposed for conducting the examination.
 

### 2019-04-17 paper.tex
edited the examination process section

@@
 We want to enable a cost-effective assessment (free for the practitioner), so we chose an online examination.
-This increases the opportunity for cheating \cite{rowe2004cheating} but we plan to deploy a several strategies to minimise the risk of cheating, such as raising the awareness of the examinees, using a pool of questions, and setting time limits for each question.
+This increases the opportunity for cheating \cite{rowe2004cheating} but we plan to deploy a several strategies to minimise the risk of cheating, such as raising the awareness of the examinees, using a pool of questions, time limits for each question and a delay between registering for and taking the examination.
 
@@
 
-The examination can be started by users any time but upon submission a delay is employed.
-Firstly, a user has to register for the examination using name and email address and optional affiliation.
-On the webpage, the process is explained, together with privacy policies.
-Further, a paragraph provides the integrity policy defining cheating and encouraging honesty.
-Practitioners are asked to opt-in the policy statement.
-With the registration, we generate an encrypted token on the server that is returned to the user by email.
+The examination process can be started at any time but a delay is employed before the examination actually starts.
+Firstly, a user has to register using their name, email address and optionally an affiliation.
+This process is explained, together with privacy policies, on the examination website. 
+Next, they need to read a paragraph on the integrity policy defining cheating and encouraging honesty.
+Practitioners are asked to opt-in for the policy statement.
+Upon receiving this registration, we generate an encrypted token on the server that is returned to the user by email.
 At this stage, we do not store any information about the user on the server.
 
-The email contains a link that will start the examination.
-The user chooses to start the examination by clicking on the link; then the information about the user and the time of starting the examination is stored in a temporary database.
+The email contains a link that will start the examination, and the user chooses to start the examination by clicking on it.
+Only then, the information about the user and the examination start time is stored in a temporary database.
 
 The summative assessment itself is conducted using multiple choice questions. 
-Therefore, for each skill, we will be developing a pool of questions but also allow contribution of questions.
-A question has more possible answers (e.g., 10) -- the practitioner has to select if each  statement is true or false.
-An examination consists of randomly selected questions and five answers per question are selected.
+Therefore, for each skill, we will develop a pool of questions and answers, and accept external contributions.
+Each question has a pool of possible answers (e.g., 10).
+An examination consists of randomly selected questions with five of their answers, and the practitioner has to decide if each statement is true or false.
 
-Once the user submits the exam results, all selected answers are stored on the server for validation -- which is done manually at the moment.
-If the user meets the criteria to pass (typically 70\% correct selection), a certificate is issued and send to the user by email.
-We then delete all personal information about the user from the server but preserve the affiliation and the raw responses.
-The affiliation is used for promotion purposes while the raw responses will be analyzed to optimize the questions.
-For example, when we identify that most users make a particular mistake, this may be an indication that the question or answer is ambivalent and needs to be improved.
+Once the user submits the completed exam, all selected answers are stored on the server for validation -- which currently is done manually.
+If the user meets the pass criteria (typically 70\% of correct answers) the earned certificate is issued and sent to the user by email.
+All personal information about the user is then deleted from the server, but the affiliation and raw responses are preserved.
+The affiliation is used for promotional purposes, while the raw responses will be analysed to optimise the questions.
+For example, if we identify that most users make the same mistake it may be an indication that either that question or its answer is too ambiguous and should be improved.
 
-If the user didn't meet the criteria to pass, we will inform him about the rough score obtained.
-The user can retry to obtain the certificate after a cooldown period (typically one week) but not immediately to prevent success via brute force methods.
-To enforce this, we keep the information about the date the exam was conducted linked to his name and email.
+If the user didn't meet the pass criteria, they will be informed about their score.
+The user can then retry to obtain the certificate after a cool-down period (typically one week), but not immediately afterwards to prevent success via brute force methods.
+To enforce this, the information about when the exam was undertaken is linked to the user's name and email.
+As the sole purpose of the multiple choice questions is the examination, the incorrectly answered questions will not revealed. 
+We assume that high quality training materials available within the HPC community, and covering the individual skills being part of this certification program, offer constructive feedback and other ways of consolidating the newly acquired knowledge.
+Therefore, the Forum's only concern is to provide the mechanism of certifying whether the learners posses that knowledge or not.
+As opposed to pointing out gaps in their understanding.
 
-As the sole purpose of the multiple choice questions is the examination, we will not reveal which questions are answered correctly.
-We assume that high quality training material for individual skills will offer multiple choice questions that serve the purpose of feedback which promotes learning  \cite{epstein2002immediate}.
+ %---> ? \cite{epstein2002immediate}.
 

### 2019-04-17 paper.tex
Anja's related work piece.

@@
 
+The SciNet Certificate Program
+\footnote{\url{https://www.scinethpc.ca/scinet-certificate-program/}}
+ provides course material for three major Computer Science topics: Scientific Computing, High Performance Computing, and Data Science each with several subcategories.
+\footnote{\url{https://support.scinet.utoronto.ca/education/mods/certificate_programs_v2/index_public.php}}
+
+Companies like NVIDIA are offering courses in deep learning\footnote{\url{https://www.nvidia.com/de-de/deep-learning-ai/education/}}.
+Also Universities like Kennesaw State University providing Online Course for their students in the areas High Performance Computing and Big Data Analytics
+\footnote{\url{https://ccse.kennesaw.edu/cs/programs/cert-hpcc.php}}.
+\footnote{\url{https://www.ece.seas.gwu.edu/graduate-certificate-high-performance-computing}}
+
 \section{Conclusion}

### 2019-04-17 paper.tex
edited the certificates section

--- 2019-04-17 paper.tex
@@
 
-Upon successful assessment, a certificate is awarded, it consists of two parts:
-A PDF with the key information needed for a meaningful certificate (for a draft, see \Cref{fig:awardedCertificate}).
-The name and identifier for the certificate is found in the center and below (here 1 and “HPC Driving License”).
-Similar to a driving license, this particular certificate could provide the minimum set of knowledge to understand and use a generic supercomputer.
+The examinees that pass the examination are awarded a corresponding certificate. Such certificate consists of two parts: a PDF and a text file. 
+The PDF contains the key information making the certificate meaningful. An example of how it may look like is presented in\Cref{fig:awardedCertificate}.
+The name and identifier of the certificate is found in the centre, on our example these are "HPC Driving License" and 1, respectively.  
+Similar to a driving license, this particular certificate could provide the minimum set of knowledge required to understand and use a typical supercomputer.
 
-Secondly, a text file is given to the user that provides the same information.
-It is PGP signed using the private key of the HPC Certification Forum to allow verification with the  public key.
-It also contains a verification URL that can be given to a third-party allowing verification of the information.
+The text file a contains the same information, as well as a verification URL that can be given to a third-party to confirm the certificate's credibility. 
+It is also PGP signed using the private key of the HPC Certification Forum to allow verification with the public key.
 
@@
 \end{verbatim}
+
+Together both documents should be able to provide enough credibility for the certification to be fully functional within the HPC academic and professional domains.
+Further improvements will be adopted as required.
 

### 2019-04-17 paper.tex
edited the training delivery section

@@
 
-We encourage the development of an ecosystem around the HPC classification, we are supporting training and tool development.
+The Forum encourages the development of an ecosystem around the HPC classification by supporting training and tool development.
+Many of its members are involved in those activities in a professional capacity, so the development of training materials and tools, and the development of the certification program have elements of co-design in them.
 
@@
 
-Firstly, an author of training material is allowed to indicate on the training material itself or on promotional material the fact
-which skills are covered by the material completely or partially.
+Firstly, an author is allowed to indicate on the training material itself or a related promotional material which skills are covered either fully or partially.
 We provide a seal that can be used for that purpose (see \Cref{fig:seal-teaching}).
-The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material
-registers a link to the material or course on our webpage using an online form. %\footnote{Details of the link will show the email address.}
+The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material registers a link to the material or course on our webpage using an online form.
+%\footnote{Details of the link will show the email address.}
 That way, the HPCCF is informed about the usage of the seal.
 
-Secondly, we will link on our webpage the endorsed training material for the individual skills and certificates.
-By using JavaScript and dynamic webpage we will provide various views on the skills with and without links to suitable training materials.
+Secondly, we will link from our webpage the endorsed training material covering the individual skills and certificates.
+By using JavaScript and dynamic webpage we will provide various views of the skills -- with and without links to suitable training materials.
 
-Note that we are not intending to verify the correct usage of the skill explicitly.
-However, in case the training material or course doesn't deliver the expected material practitioners may complain and we will remove the training material from our webpage.
+Note that we are not intending to verify the correct usage of the seal explicitly.
+However, in case the training material or course doesn't deliver the expected material practitioners may complain and we will remove the link to that training material from our webpage.
 
-We expect that this strategy will lead to the availability of good free training material for most skills while companies and individuals can still charge for effective training courses.
-Ultimately, the resulting training material will complement each other leading to a rich variety of content suitable for each individual practitioner, e.g., addressing different learning styles and languages.
+We expect that this strategy will make a good range of free training material available for most skills, while various institutions and individuals can still charge for effective training courses.
+Ultimately, the catalogued training materials will complement each other, leading to a rich variety of content suitable for each individual practitioner, e.g., addressing different learning styles and languages.
+This becomes increasingly important as more in-time personalised training in needed by our ever-growing HPC community.
 

### 2019-04-17 paper.tex
edited the Navigation section

@@
 There is a generally accepted set of skills and competencies necessary to efficiently use HPC resources.
-This skill set depends on the role and domain of the practitioner but also on the available infrastructure of the center providing the computing resources.
+This skill set depends on the role and domain of the practitioner but also on the available infrastructure of the centre providing the computing resources.
 For example, a scientist needing to run an application on a specific machine may need basic skills in Linux, MPI, environment modules, and knowledge about the batch scheduler, e.g., Slurm.
@@
 
- %---> ? \cite{epstein2002immediate}.
+ %---> ? \cite{epstein2002immediate}. Not sure this still fits here [WF]
 
@@
 %\paragraph{Navigation}
-Thanks to the contributions of the PeCoH project, a JavaScript prototype enables the embedding of a navigable skill tree into a webpage.
-The script can be used by different stackholders to present their own view on the skill-tree.
-By view we mean the selection and organization of the skills, and the additional information provided when navigating the tree.
-For instance, you could have a tree for a specific scientific domain, for a specific data center, or even for the role of the tester of a specific application; it could indicate which skills are mandatory or beneficial for these use cases, providing links to training material or adding further supplementary information.
+Thanks to the contributions of the PeCoH project, a JavaScript prototype embeds a navigable skill tree into a webpage.
+The script can be used by different stakeholders to adjust and present the skill tree in the most suitable for them view.
+By view we mean the selection and organisation of the skills, and the additional information provided when looking at the tree.
+For instance, you could have a tree for a specific scientific domain, for a specific data centre, or even for the role of the tester of a specific application. 
+This feature could be used to indicate which skills are mandatory or beneficial for these use cases, providing links to training material or adding further supplementary information.
 

### 2019-04-17 paper.tex
edited half of the related work section

@@
 
-Relevant work can be classified into approaches to establish a curriculum or the creation of teaching material.
-In academia, individual universities offer their own curriculum around scientific computing and HPC, covering theoretical aspects like the software development of numerical applications.
-They are not tailored to the needs of a practitioner to actually use HPC systems effectively.
-Data centers offer their own material and courses to support their own users.
+Relevant work can be divided into two categories: efforts to establish an HPC curriculum, and systematic efforts to design, develop and deliver HPC teaching and training materials.
+
+In academia, many universities offer their own curriculum around scientific computing and HPC as part of their undergraduate programmes, covering a range of theoretical and practical aspects relevant to the students field of study, e.g.
+software development of numerical domain-specific applications.
+Such courses rarely cover the efficient and effective use of HPC systems. 
+The number of taught postgraduate courses focusing on HPC is small, and the number of the whole programmes dedicated to HPC is even smaller. % could probably list ~5
+
+Data centres offer their own teaching materials and run a number of training courses to support their own users. 
+Although, these are becoming more varied in content and more accessible through the adoption of online, remote and asynchronous delivery methods, they are still not enough to fulfil the training needs of our community.
+Due to a variety of reasons some training opportunities are still only available at a specific time or place, or simply do not scale well enough to satisfy the demand for them.
+
+% ------------ Below not edited 
 Several projects address the generation and sharing of teaching material for HPC.

### 2019-04-18 paper.tex
edited/extended the related work section

@@
 
-\jk{Please everyone!}
-
 Relevant work can be divided into two categories: efforts to establish an HPC curriculum, and systematic efforts to design, develop and deliver HPC teaching and training materials.
 
-In academia, many universities offer their own curriculum around scientific computing and HPC as part of their undergraduate programmes, covering a range of theoretical and practical aspects relevant to the students field of study, e.g.
+In academia, many universities offer their own curriculum around scientific computing and HPC, as part of their undergraduate programmes, covering a range of theoretical and practical aspects relevant to the students field of study, e.g.
 software development of numerical domain-specific applications.
 Such courses rarely cover the efficient and effective use of HPC systems. 
-The number of taught postgraduate courses focusing on HPC is small, and the number of the whole programmes dedicated to HPC is even smaller. % could probably list ~5
+The number of taught modules focusing on HPC is small, and the number of the whole programmes dedicated to HPC is even smaller.
+We are aware such programmes are run by: EPCC at the University of Edinburgh \footnote{\url{https://www.epcc.ed.ac.uk/msc}}, the University of Liverpool\footnote{\url{https://www.liverpool.ac.uk/study/postgraduate-taught/taught/big-data-msc/overview/}}, the International School for Advanced Studies (SISSA) and ICTP in Italy\footnote{\url{https://www.mhpc.it/}}, the Trinity Collage Dublin\footnote{\url{https://www.maths.tcd.ie/hpcmsc/}} in Ireland, the Polytechnic University of Catalonia\footnote{\url{https://masters.fib.upc.edu/masters/miri-high-performance-computing}} and BSC in Spain and the University of Cote d'Azur\footnote{\url{http://univ-cotedazur.fr/education/training?AIHPC18&lang=en}} in France.
+These 1-2 year master programmes are fully accredited by the universities that run them, but that also makes them fairly expensive and their comprehensiveness is not suitable for the majority of HPC users.
 
@@
 Although, these are becoming more varied in content and more accessible through the adoption of online, remote and asynchronous delivery methods, they are still not enough to fulfil the training needs of our community.
-Due to a variety of reasons some training opportunities are still only available at a specific time or place, or simply do not scale well enough to satisfy the demand for them.
+Due to a variety of reasons some training opportunities are still only available at a specific time or place, or simply do not scale well enough to satisfy the demand.
 
-% ------------ Below not edited 
-Several projects address the generation and sharing of teaching material for HPC.
-The EuroLab-4-HPC project establishes training in form of (online) courses\footnote{\url{https://www.eurolab4hpc.eu/}}.
+Several projects, organisations and initiatives continue to put their efforts into developing and sharing of teaching HPC resources. 
+The EuroLab-4-HPC project establishes training in form of online courses\footnote{\url{https://www.eurolab4hpc.eu/}}.
 The Barcelona Supercomputing Centre (BSC) aims to develop a professional training curriculum \cite{sancho2016bsc}.
-The virtual organization XSEDE\footnote{\url{https://portal.xsede.org/web/xup/training/overview}} provides an online system to train the usage of an HPC system, structuring the corresponding information on their website into major topics like “Getting Started”.
-The user can navigate the topics and receive further information.
+Both XSEDE\footnote{\url{https://portal.xsede.org/web/xup/training/overview}} (The Extreme Science and Engineering Discovery Environment) and PRACE\footnote{\url{http://www.training.prace-ri.eu/}} (Partnership for Advanced Computing in Europa), serving similar purpose in US and Europe, provide a variety of training opportunities and resources to make HPC more accessible to researchers across many scientific domains.
+The SciNet Certificate Program\footnote{\url{https://www.scinethpc.ca/scinet-certificate-program/}} provides course material for three major Computer Science topics: Scientific Computing, High Performance Computing, and Data Science each with several subcategories.
+Whereas the initiatives such as the HPC University\footnote{\url{http://hpcuniversity.org}}, the Carpentries (the HPC Carpentry especially)\footnote{\url{https://hpc-carpentry.github.io/}} and ACM SIGHPC Education Chapter\footnote{\url{https://sighpceducation.acm.org/}} strive to make sharing of teaching resources and practices simpler, and more accessible to trainers and practitioners alike.
 
-The SciNet Certificate Program
-\footnote{\url{https://www.scinethpc.ca/scinet-certificate-program/}}
- provides course material for three major Computer Science topics: Scientific Computing, High Performance Computing, and Data Science each with several subcategories.
-\footnote{\url{https://support.scinet.utoronto.ca/education/mods/certificate_programs_v2/index_public.php}}
-
-Companies like NVIDIA are offering courses in deep learning\footnote{\url{https://www.nvidia.com/de-de/deep-learning-ai/education/}}.
-Also Universities like Kennesaw State University providing Online Course for their students in the areas High Performance Computing and Big Data Analytics
-\footnote{\url{https://ccse.kennesaw.edu/cs/programs/cert-hpcc.php}}.
-\footnote{\url{https://www.ece.seas.gwu.edu/graduate-certificate-high-performance-computing}}
+Finally, many companies offer training courses making their products and services easier to use by their end-users, e.g.
+NVIDIA offering courses in deep learning\footnote{\url{https://www.nvidia.com/de-de/deep-learning-ai/education/}} or Arm offering courses on various arm technologies\footnote{\url{https://www.arm.com/support/training}}.
+%Also Universities like Kennesaw State University providing Online Course for their students in the areas High Performance Computing and Big Data Analytics
+%\footnote{\url{https://ccse.kennesaw.edu/cs/programs/cert-hpcc.php}}.
+%\footnote{\url{https://www.ece.seas.gwu.edu/graduate-certificate-high-performance-computing}}  --> many universities do that, do we want to list all of them?
 

### 2019-04-18 paper.tex
edited/extened the benefits section

@@
 
-This allows the re-use of existing content but also allows to create a new ecosystem in which HPC centers or commercial companies could offer the best teaching material.
-Teaching material should be marked to indicated which skills it covers.
+The HPC Certification Program allows the re-use of existing content but also makes it possible to create a new ecosystem in which HPC centres, research labs, academic institutions and commercial companies could offer the best of their teaching material.
+The existing or newly created teaching resources should be marked accordingly to indicated which skills they covers.
 In the future, the program may provide means to register and reference existing content of third-parties allowing users to browse the skills and navigate to teaching material.
@@
 
-HPC practitioners
-Increase motivation to participate
-(Certificates are recognized in CV)
-Validate knowledge via tests
-Browse of relevant competencies
-Identify recommended and required skills
-Compare teaching offers across sites
-Data centers
+The program brings multiple benefits to everyone involved in HPC teaching and training.
+It's obvious that making clear what skills are required or recommended for a competent HPC user would be helpful to both the HPC service providers and practitioners.
+Training providers could bundle together skills that are most beneficial for specific user roles and scientific domains, which would allow practitioners to browse through skills to quickly identify and learn the skills required to perform their tasks.
+The variety of training offered within our community makes finding the right resources more complicated than it should be -- the certification program will provide useful information where the desired skills could be learnt.
+The examination confirming that a certain set of competencies has been acquired makes the learning process more complete and meaningful.
 
-Increase sharing of teaching materials
-Documentation of taught skills simplified
-Identify missing teaching activities
-Tailor skill-tree specifically to users
-Correlate lack of skills with efficient us\kh{diese Subsection ist vermutlich noch in Arbeit; Groß-/ Kleinschreibung?}
-
-Making clear what skills are required of or recommended for a competent HPC user would benefit both the HPC service providers and practitioners.
-Moreover, it would allow centres to bundle together skills that are most beneficial for specific user roles and scientific domains.
-From the perspective of content providers, existing training material can be mapped to competencies allowing users to quickly identify and learn the skills they require.
-Finally, the certificates recognized by the whole HPC community simplify inter-comparison of independently offered courses and provide additional incentive for participation.
+By participating in the program the HPC training providers can increase the visibility of their teaching opportunities and share their resources more effectively. 
+The mapping of the skills defined by the program onto the existing training materials should also help to identify any potential gaps and improve the integrity of offered training. 
+Finally, the certificates recognised by the whole HPC community simplify inter-comparison of independently offered courses and provide additional incentive for participation.
+Overall, the flexibility of the program allows to construct more personalised and just-in-time pathways to learning about HPC.
 

### 2019-04-19 paper.tex
small edit
Last iteration

@@
 \author{Kai Himstedt}
-\author{Nathanael Hübbe}
 \affiliation{%
@@
 
-With the HPC Certification Forum we aim to clearly categorise, define, and examine competencies expected from proficient HPC practitioners.
+With the HPC Certification Forum, we aim to clearly categorise, define, and examine competencies expected from proficient HPC practitioners.
 In this article, we report the status and progress this independent body has made during the first year of its existence. The drafted processes and prototypes are expected to mature into a
@@
 
-Most institutions operating HPC systems offer regular training events focusing on general aspects of their supercomputer's hardware architecture, software stack, application development environment  and various tuning and debugging tools.
-It is understandable why the materials they are geared towards the special demands of the institutions they support and its specific HPC environment.
-The problem is that teaching content typically covers only a small part of basic HPC skills necessary to use other HPC systems.
-This approach of teaching only specific implementations, tools or workflows, instead of concepts behind them makes a move to a different system or tool unnecessary complicated.
-Narrowing the scope of training events make sense from the HPC provider perspective, but is not very conducive to development of more comprehensive learning environment that provides assessment and certifies the newly acquired skills.
-So although, certificates are used widely in IT industry to verify certain knowledge, until now there was no similar approach for HPC training.
+Most data centers operating HPC systems offer regular training events focusing on general aspects of their supercomputer's hardware architecture, software stack, application development environment and various tuning and debugging tools.
+It is understandable why the materials they offer are geared towards the special demands of the specific HPC environment and the institutions they support.
+The problem is that teaching content typically covers only a fraction of the HPC skills necessary to use another HPC system.
+This approach of teaching only specific implementations, tools or workflows---instead of concepts behind them---makes a move to a different system or tool unnecessary complicated.
+Narrowing the scope of training events make sense from the HPC provider perspective, but is not very conducive to development of a more comprehensive learning environment that provides assessment and certifies the newly acquired skills.
+Although certificates are used widely in IT industry to verify certain knowledge, until now there was no similar approach for HPC training.
 It is, however, clear that a mapping of competences and certification scheme could address some of the challenges stemming from the constantly growing training needs of our community,
 
-This article describes the current status of the certification program initiated by the HPC Certification Forum.
+This article describes the current status of the certification program curated by the HPC Certification Forum.
 Our previous work provided a brief overview of the evolution from the project that sparked the HPC Certification Forum \cite{TAHCPKHHSS19} while this article provides details on adopted mechanisms and design decisions.
@@
 
-The forum is organised around a Webpage\footnote{http://hpc-certification.org},  a GitHub repository\footnote{https://github.com/HPC-certification-forum},  and a could-based team collaboration tool (Slack) for communication and monthly meetings.
-The membership is divined into three categories: associate, full and steering board.
+The forum is organised around a Webpage\footnote{http://hpc-certification.org},  a GitHub repository\footnote{https://github.com/HPC-certification-forum},  and a team collaboration tool (Slack) for communication and monthly meetings.
+The membership is divided into three categories: associate, full and steering board.
 Anyone can become an associate member free of charge, allowing a passive involvement -- e.g., observing the status, being listed on the webpage.
-Full members must actively contribute to the program and have voting rights for the roles of the steering board.
+Full members must actively contribute to the program and, in return, gain voting rights for the roles of the steering board.
 The steering board directs the overall activities and is organised in different responsibilities, i.e., into topic-specific chairs. At the moment the steering board has 9 members.
@@
 Slack is also used to conduct our monthly open meetings between members and the steering board.
-At beginning video conferencing tools have been used, but the geographical diversity of the attendees influenced the decision to move towards chat-based tools.
+At beginning, video conferencing tools have been used but the geographical diversity of the attendees influenced the decision to move towards chat-based tools.
 The asynchronous nature and automatic message retention proved to be more productive, and provided a more open and inclusive platform for discussion.
-Meeting notes with action items are extracted from Slack and documented using Google Doc (an online word processor allowing a real-time and multiple-user collaboration).
+Meeting notes with action items are extracted from Slack and documented using Google Doc (an online word processor allowing real-time and multiple-user collaboration).
 
@@
 
-This model can be compared to the classification of school knowledge, for example, a skill with the name “basic arithmetic operations” would include the math skills of addition (being able to add numbers), subtraction (being able to subtract numbers), multiplication (being able to multiply numbers) and division (being able to divide numbers).
-Operating on two numbers would be a basic level of the skill, whereas mentally operating on hundreds of numbers would be an expert level.
-Another example could be a skill called "technical drawing", in which being able to draw simple geometric figures would be counted as a basic level, and an ability to draw a complicated mechanical objects would be an expert level.
-
 The basic level should cover the most relevant aspect of the skill (needed by anyone that uses the skill), whereas the intermediate (used for common exceptional cases) and expert levels (used in special circumstances)  are needed only for a subset of users.
@@
 
+This model can be compared to the classification of school knowledge, for example, a skill with the name “basic arithmetic operations” would include the math skills of addition (being able to add numbers) and subtraction (being able to subtract numbers), multiplication (being able to multiply numbers) and division (being able to divide numbers).
+Operating on two numbers with $\pm$ would be a basic level of the skill, whereas including multiplication/division and mentally operating on hundreds of numbers would be an expert level.
+Another example could be a skill called "technical drawing", in which being able to draw simple geometric figures would be counted as a basic level, and an ability to draw a complicated mechanical objects would be an expert level.
+
 The skills are organised in a tree structure from a coarse-grained to a fine-grained representation, allowing users to browse the skill based on the semantics.
-The root level of our current skill tree is shown in \Cref{fig:skill-tree}. The goal is to finalise the tree this year.
+The root level of our current\footnote{The goal is to finalise the tree this year.} skill tree is shown in \Cref{fig:skill-tree}.
 The basic idea is that the skills from the root level simplify the navigation by providing an indication about their scope, e.g., core knowledge, usage of HPC environments, or about programming.
@@
 \begin{itemize}
-  \item \textbf{ID}: ID according to its position in the skill tree. The last character indicates the level of the skill (Basic, Intermediate, or Advanced).
+  \item \textbf{ID}: Identifier according to its position in the skill tree.
+  The last character indicates the level of the skill (Basic, Intermediate, or Advanced).
   \item \textbf{Name}: A name capturing the essence of the skill.
@@
 Hussey et al.\cite{hussey2008learning} categorised the aggregation of skills into the following levels: individual teaching events, specified for modules or short courses, and those specified for whole degree programmes.
-Although, Hussey et al.
-conclude that LOs on the coarse grained level are not useful for high-level education, using a similar concept with relaxed level of granularity/abstraction of the learning outcome fits well within the framework of the certification program.
-\kh{den Satz habe ich nicht genau verstanden; als Leser würde ich mir die Kurzbegründung wünschen, die Hussey et al. für ihre Feststellung anführen}
+Hussey et al.
+conclude that LOs on the coarse grained level are not useful for high-level education because they “would state little more than an annotated list of contents” and relevant for those familiar with the subject.
+To overcome these issues, we provide a relaxed level of granularity and lower level of abstraction of the learning outcomes on inner nodes.
 
@@
 
-\ag{When I was reading the "learning outcome" of USE4.2B, another category came to mind:
-How to write job scripts? How to batch use?
-So why not create a case where the learning outcomes overlap?
-Since you did the skill examples with USE4.2 in 4.2, I would not do "Figure 1" with extension of PE4 but USE4.
-Then you can always look there.
-}
-
 The next leaf-level skill describes how workload management works in general, regardless of the specific software implementing it.
-The aim and outcomes defined by the parent skill (described above) are expected to be covered (to a certain extend) and refined by this leaf skill.
+The aim and outcomes defined by the parent skill (described above) are expected to be covered to a certain extend and refined by this leaf skill.
 
@@
   \item comprehend the exclusive and shared usage model in HPC;
+  \item explain the generic steps required to run and monitor a single job;
   \item differentiate between the batch and interactive job submission;
@@
   \item explain the role of environment variables as a mean to communicate certain settings of your job;
-  \item comprehend job budgeting and accounting principles;
-  \item explain the generic steps required run and monitor a single job.
+  \item comprehend job budgeting and accounting principles.
   \end{itemize}
@@
 
-\ag{I could put my slide set online and show the skill tree for the slide set. An example could be shown, there the content described in a skill tree are also explained in slide sets.
-Everything under USE 4.2.2 B, I have explained it in my slide set under "Slurm Usage on Goethe HLR cluster".
-\\
-What I have found and would like to try it out:  http://xlong88.github.io/draw-binary-tree-latex/
-Create recursive and automatically a Binary Tree with Tikz and Tikz-qtree.
-If we can do it generically then I will be one step ahead with my skill tree for the slide set.
-}
+%\ag{I could put my slide set online and show the skill tree for the slide set. An example could be shown, there the content described in a skill tree are also explained in slide sets.
+%Everything under USE 4.2.2 B, I have explained it in my slide set under "Slurm Usage on Goethe HLR cluster".
+%What I have found and would like to try it out:  http://xlong88.github.io/draw-binary-tree-latex/
+%Create recursive and automatically a Binary Tree with Tikz and Tikz-qtree.
+%If we can do it generically then I will be one step ahead with my skill tree for the slide set.
 
 The learning outcomes of this skill, marked with B to indicate its basic level, are focusing on the most fundamental knowledge required to use Slurm effectively.
-An intermediate version of the skill could, for example, cover how to create reservations or special queues.
+An intermediate version of the skill could, for example, could cover how to create reservations or special queues.
 
@@
 
-A certificate shall serve as a confirmation that a user obtain the expertise in the relevant skills.
+A certificate shall serve as a confirmation that a user obtained the expertise in the relevant skills.
 Special considerations needs to be given to the certification integrity.
@@
 The questions are the only proprietary component for the HPCCF -- using restrictive license terms for authors while giving them credit.
-This is considered necessary to minimise the overhead of managing the database containing solutions to the examination questions.
+This is considered necessary for managing the database containing solutions to the examination questions.
 
@@
 Upon receiving this registration, we generate an encrypted token on the server that is returned to the user by email.
-At this stage, we do not store any information about the user on the server.
+Up to this stage, we do not store any information about the user on the server.
 
@@
 
-Once the user submits the completed exam, all selected answers are stored on the server for validation -- which currently is done manually.
+Once the user submits the completed exam, the selection of answers is stored on the server for validation.
+At the moment, we envision the validation process includes a final manual step to trigger the certificate generation once provided with all information.
 If the user meets the pass criteria (typically 70\% of correct answers) the earned certificate is issued and sent to the user by email.
@@
 We assume that high quality training materials available within the HPC community, and covering the individual skills being part of this certification program, offer constructive feedback and other ways of consolidating the newly acquired knowledge.
-Therefore, the Forum's only concern is to provide the mechanism of certifying whether the learners posses that knowledge or not.
+Therefore, the Forum's only concern is to provide the mechanism of certifying whether the learners posses that knowledge or not;
 As opposed to pointing out gaps in their understanding.
@@
 The examinees that pass the examination are awarded a corresponding certificate. Such certificate consists of two parts: a PDF and a text file.
-The PDF contains the key information making the certificate meaningful. An example of how it may look like is presented in\Cref{fig:awardedCertificate}.
-The name and identifier of the certificate is found in the centre, on our example these are "HPC Driving License" and 1, respectively.  
+The PDF contains the key information making the certificate meaningful. An example of how it may look like is presented in \Cref{fig:awardedCertificate}.
+The name and identifier of the certificate is found in the centre, on our example these are "HPC Driving License" and ID 1, respectively.
 Similar to a driving license, this particular certificate could provide the minimum set of knowledge required to understand and use a typical supercomputer.
@@
 The text file a contains the same information, as well as a verification URL that can be given to a third-party to confirm the certificate's credibility.
-It is also PGP signed using the private key of the HPC Certification Forum to allow verification with the public key.
-
-The file looks as follows:
+It is also PGP signed using the private key of the HPC Certification Forum to allow verification with the public key. An example file looks as follows:
 \begin{verbatim}
@@
 We provide a seal that can be used for that purpose (see \Cref{fig:seal-teaching}).
-The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material registers a link to the material or course on our webpage using an online form.
+The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material registers a link to the material (or course) on our webpage using an online form.
 %\footnote{Details of the link will show the email address.}
@@
 Secondly, we will link from our webpage the endorsed training material covering the individual skills and certificates.
-By using JavaScript and dynamic webpage we will provide various views of the skills -- with and without links to suitable training materials.
+By using JavaScript and dynamic webpages, we will provide various views of the skills -- with and without links to suitable training materials.
 
@@
 
-\subsection{Navigation}\kh{Vorschlag Unterkapitel in "Results" umbenennen oder an anderer Stelle aus "Erwartungsgründen" ein "Results"-Kapitel ergänzen (am besten natürlich auf der Hauptgliederungsebene, aber das wird vermutlich schwierig werden)}
+\subsection{Navigation}
+
 %\paragraph{Navigation}
@@
 
-In academia, many universities offer their own curriculum around scientific computing and HPC, as part of their undergraduate programmes, covering a range of theoretical and practical aspects relevant to the students field of study, e.g.
-software development of numerical domain-specific applications.
+In academia, many universities offer their own curriculum around scientific computing and HPC, as part of their undergraduate programmes, covering a range of theoretical and practical aspects relevant to the students field of study, e.g., software development of numerical domain-specific applications.
 Such courses rarely cover the efficient and effective use of HPC systems.
 The number of taught modules focusing on HPC is small, and the number of the whole programmes dedicated to HPC is even smaller.
-We are aware such programmes are run by: EPCC at the University of Edinburgh \footnote{\url{https://www.epcc.ed.ac.uk/msc}}, the University of Liverpool\footnote{\url{https://www.liverpool.ac.uk/study/postgraduate-taught/taught/big-data-msc/overview/}}, the International School for Advanced Studies (SISSA) and ICTP in Italy\footnote{\url{https://www.mhpc.it/}}, the Trinity Collage Dublin\footnote{\url{https://www.maths.tcd.ie/hpcmsc/}} in Ireland, the Polytechnic University of Catalonia\footnote{\url{https://masters.fib.upc.edu/masters/miri-high-performance-computing}} and BSC in Spain and the University of Cote d'Azur\footnote{\url{http://univ-cotedazur.fr/education/training?AIHPC18&lang=en}} in France.
+We are aware such programmes are run by: EPCC at the University of Edinburgh\footnote{\url{https://www.epcc.ed.ac.uk/msc}}, the University of Liverpool\footnote{\url{https://www.liverpool.ac.uk/study/postgraduate-taught/taught/big-data-msc/overview/}}, the International School for Advanced Studies (SISSA) and ICTP in Italy\footnote{\url{https://www.mhpc.it/}}, the Trinity Collage Dublin\footnote{\url{https://www.maths.tcd.ie/hpcmsc/}} in Ireland, the Polytechnic University of Catalonia\footnote{\url{https://masters.fib.upc.edu/masters/miri-high-performance-computing}} and BSC in Spain and the University of Cote d'Azur\footnote{\url{http://univ-cotedazur.fr/education/training?AIHPC18&lang=en}} in France.
 These 1-2 year master programmes are fully accredited by the universities that run them, but that also makes them fairly expensive and their comprehensiveness is not suitable for the majority of HPC users.
+
+\medskip
 
@@
 Due to a variety of reasons some training opportunities are still only available at a specific time or place, or simply do not scale well enough to satisfy the demand.
+
+\medskip
 
@@
 The HPC Certification Program allows the re-use of existing content but also makes it possible to create a new ecosystem in which HPC centres, research labs, academic institutions and commercial companies could offer the best of their teaching material.
-The existing or newly created teaching resources should be marked accordingly to indicated which skills they covers.
+According to our proposal, the existing and newly created teaching resources should be marked accordingly to indicated which skills they cover.
 In the future, the program may provide means to register and reference existing content of third-parties allowing users to browse the skills and navigate to teaching material.
@@
 \small
-We are thankful for the contributions and discussions with the members of the HPCCF and for the contributions made by the PeCoH project.
-\jk{TODO}
+We are thankful for the contributions and discussions with the members of the HPCCF and for the contributions made by the PeCoH project particularly Nathanael Hübbe for developing tools.
 PeCoH was supported by the German Research Foundation (DFG) under grants LU 1353/12-1, OL 241/2-1, and RI 1068/7-1.

### 2019-04-26 paper.tex
Reviewer 3 typos fixed.

@@
 For example, a scientist needing to run an application on a specific machine may need basic skills in Linux, MPI, environment modules, and knowledge about the batch scheduler, e.g., Slurm.
-Now rather than providing that scientists with a list of instructions to be followed in a copy and paste fashion or a never-ending list of things they should know, we want them to understand each of the required steps without having to learner everything about it, but at the same time understand how it fits into the bigger picture of using an HPC system.
+Now rather than providing that scientists with a list of instructions to be followed in a copy and paste fashion or a never-ending list of things they should know, we want them to understand each of the required steps without having to learn everything about it, but at the same time understand how it fits into the bigger picture of using an HPC system.
 For instance, understanding Slurm is a good example of a very fine-grained skill that fits under a more generic skill defined as "resource management", illustrating concepts across the rich variety of available resource managers.
@@
 As the tree serves the purpose of organising the skills, the references from one branch to a skill in another branch are allowed.
-This import feature makes the reuse of the skill definitions possible, at the same time allowing users to navigate the tree according to the semantics.
+This important feature makes the reuse of the skill definitions possible, at the same time allowing users to navigate the tree according to the semantics.
 
@@
 The learning outcomes of this skill, marked with B to indicate its basic level, are focusing on the most fundamental knowledge required to use Slurm effectively.
-An intermediate version of the skill could, for example, could cover how to create reservations or special queues.
+An intermediate version of the skill could, for example, cover how to create reservations or special queues.
 
@@
 To enforce this, the information about when the exam was undertaken is linked to the user's name and email.
-As the sole purpose of the multiple choice questions is the examination, the incorrectly answered questions will not revealed.
+As the sole purpose of the multiple choice questions is the examination, the incorrectly answered questions will not be revealed.
 We assume that high quality training materials available within the HPC community, and covering the individual skills being part of this certification program, offer constructive feedback and other ways of consolidating the newly acquired knowledge.
@@
 
-The text file a contains the same information, as well as a verification URL that can be given to a third-party to confirm the certificate's credibility.
+The text file contains the same information, as well as a verification URL that can be given to a third-party to confirm the certificate's credibility.
 It is also PGP signed using the private key of the HPC Certification Forum to allow verification with the public key. An example file looks as follows:
@@
 Training providers could bundle together skills that are most beneficial for specific user roles and scientific domains, which would allow practitioners to browse through skills to quickly identify and learn the skills required to perform their tasks.
-The variety of training offered within our community makes finding the right resources more complicated than it should be -- the certification program will provide useful information where the desired skills could be learnt.
+The variety of training offered within our community makes finding the right resources more complicated than it should be -- the certification program will provide useful information where the desired skills could be learned.
 The examination confirming that a certain set of competencies has been acquired makes the learning process more complete and meaningful.
